### 2013-11-06 paper/main.tex
Initial commit.

\documentclass{proc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{fixltx2e}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{url}
\usepackage{amsmath}
\usepackage{mathrsfs}

\title{
The Small World Network Effect in Open Source Project Teams
\author{Kevin Peterson\\
\small \texttt{pete1968@umn.edu}
}
}

\begin{document}
\maketitle

\begin{abstract}
Team cohesion and the dynamics of team forming are important parts of any project, with software projects being no exception. An interesting aspect of team building is the relationships formed between the team members. If follows that visualizing software team members as a graph can give some insight as to what the optimal team conditions are. As team members move between projects, these graphs gets more and more connected as team members make connections. We show that this connectivity, known as the "small world effect," has a positive impact on team performance at when the connectivity levels are moderate. This aligns with similar research findings of non-software teams. We do, however, find high performance at the extremes of the connectivity range.
\end{abstract}

\noindent \\\textbf{Keywords.} Git, GitHub, Open Source

\section{Introduction}

\subsection{Hypotheses}

\section{Methods}
\subsection{Collection and Storage}

\subsection{Analysis}

\section{Results}

\subsection{Quantitative}

\subsection{Qualitative}

\section{Conclusion}
\section{Acknowledgments}

\bibliographystyle{plain}
\bibliography{bibliography}

\end{document}

### 2013-11-06 code/analyze_graph.py

@@ -1,0 +1,183 @@
+import networkx as nx
+import csv
+import itertools
+import matplotlib.pyplot as plt
+import random
+import numpy as np
+import MySQLdb
+from scipy import stats
+
+
+def read_github():
+    contributors = {}
+    projects = {}
+    popularity = {}
+    csvreader = csv.DictReader(open('../data/combined.csv'), delimiter=',')
+    for row in csvreader:
+        watchers = row['repository_watchers']
+        project = row['repository_url']
+        popularity[project] = watchers
+        contributor = row['actor_attributes_login']
+        if contributor not in contributors:
+            contributors[contributor] = []
+        if project not in projects:
+            projects[project] = []
+
+        contributors[contributor].append(project)
+        projects[project].append(contributor)
+
+    return contributors, projects, popularity
+
+def reject_outliers(data):
+    return data
+
+def get_small_worldness(q_dict_g, q_dict_rand):
+    """
+    Humphries, M. D., & Gurney, K. (2008).
+    Network 'small-world-ness': a quantitative method for determining canonical network equivalence. PLoS One, 3(4), e0002051.
+    """
+    try:
+        C_g = q_dict_g['cc']
+        C_rand = q_dict_rand['cc']
+
+        L_g = q_dict_g['pl']
+        L_rand = q_dict_rand['pl']
+
+        return (C_g/C_rand) / (L_g/L_rand)
+    except ZeroDivisionError:
+       return None
+
+
+def compute_q(graph):
+    cc = nx.transitivity(graph)
+    pl = nx.average_shortest_path_length(graph)
+
+    return {"q":cc/pl,"pl":pl,"cc":cc}
+
+def compute_random_graph(graph):
+    nodes = graph.number_of_nodes()
+    edges = graph.number_of_edges()
+
+    graph_r = nx.Graph()
+
+    node_range = range(0,nodes)
+
+    last_node = None
+    for i in node_range:
+        if last_node is None:
+            last_node = i
+        else:
+            graph_r.add_edge(last_node,i)
+            last_node = i
+
+    while graph_r.number_of_edges() < edges:
+        node1 = random.choice(node_range)
+        node2 = random.choice(node_range)
+
+        if node1 != node2:
+            graph_r.add_edge(node1,node2)
+
+    return graph_r
+
+
+def graph(name, contributors_projects, popularity):
+
+    contributors = contributors_projects[0]
[…]

### 2013-11-06 paper/publish.sh

@@ -1,0 +1,1 @@
+latexmk main.tex -output-directory=build -pdf

### 2013-11-07 code/analyze_graph.py
Added a table creator.

@@ -4,9 +4,7 @@ import itertools
 import matplotlib.pyplot as plt
 import random
 import numpy as np
-import MySQLdb
-from scipy import stats
-
+import math
 
 def read_github():
     contributors = {}
@@ -14,9 +12,13 @@ def read_github():
     popularity = {}
     csvreader = csv.DictReader(open('../data/combined.csv'), delimiter=',')
     for row in csvreader:
-        watchers = row['repository_watchers']
+        if row['repository_fork'] == 'true':
+            continue
+
+        forks = int(row['repository_forks'])
+        watchers = int(row['repository_watchers'])
         project = row['repository_url']
-        popularity[project] = watchers
+        popularity[project] = int(math.sqrt(forks * watchers))
         contributor = row['actor_attributes_login']
         if contributor not in contributors:
             contributors[contributor] = []
@@ -62,6 +64,8 @@ def compute_random_graph(graph):
 
     node_range = range(0,nodes)
 
+    random_edges = 0
+
     last_node = None
     for i in node_range:
         if last_node is None:
@@ -70,12 +74,13 @@ def compute_random_graph(graph):
             graph_r.add_edge(last_node,i)
             last_node = i
 
-    while graph_r.number_of_edges() < edges:
+    while random_edges < edges:
         node1 = random.choice(node_range)
         node2 = random.choice(node_range)
 
         if node1 != node2:
             graph_r.add_edge(node1,node2)
+            random_edges += 1
 
     return graph_r
 
@@ -99,6 +104,7 @@ def graph(name, contributors_projects, popularity):
 
     q = []
     popularity_score = []
+    small_worldness = []
 
     def sample_graphs(subgraphs):
         return subgraphs
@@ -107,6 +113,12 @@ def graph(name, contributors_projects, popularity):
         if subgraph.number_of_nodes() < 3: continue
 
         graph_q = compute_q(subgraph)
+
+        random_graph = compute_random_graph(subgraph)
+
+        random_q = compute_q(random_graph)
+
+        small_worldness.append(get_small_worldness(graph_q, random_q))
 
         q.append(graph_q['q'])
 
@@ -122,8 +134,8 @@ def graph(name, contributors_projects, popularity):
 
         popularity_score.append(avg_popularity)
 
-    bins = [round(float(i)*.1,2)/2 for i in range(0,21)]
[…]

### 2013-11-08 code/analyze_graph.py
Added tables.

@@ -5,6 +5,7 @@ import matplotlib.pyplot as plt
 import random
 import numpy as np
 import math
+import table
 
 def read_github():
     contributors = {}
@@ -56,9 +57,7 @@ def compute_q(graph):
 
     return {"q":cc/pl,"pl":pl,"cc":cc}
 
-def compute_random_graph(graph):
-    nodes = graph.number_of_nodes()
-    edges = graph.number_of_edges()
+def compute_random_graph(nodes, edges):
 
     graph_r = nx.Graph()
 
@@ -103,24 +102,37 @@ def graph(name, contributors_projects, popularity):
                 G.add_edge(e0,e1)
 
     q = []
+    cc = []
+    pl = []
     popularity_score = []
     small_worldness = []
+    subgraph_node_number = []
+    subgraph_edge_number = []
 
     def sample_graphs(subgraphs):
         return subgraphs
 
-    for subgraph in sample_graphs(nx.connected_component_subgraphs(G)):
+    subgraphs = sample_graphs(nx.connected_component_subgraphs(G))
+    for subgraph in subgraphs:
         if subgraph.number_of_nodes() < 3: continue
+
+        nodes = subgraph.number_of_nodes()
+        edges = subgraph.number_of_edges()
+
+        subgraph_node_number.append(nodes)
+        subgraph_edge_number.append(edges)
 
         graph_q = compute_q(subgraph)
 
-        random_graph = compute_random_graph(subgraph)
+        random_graph = compute_random_graph(nodes, edges)
 
         random_q = compute_q(random_graph)
 
         small_worldness.append(get_small_worldness(graph_q, random_q))
 
         q.append(graph_q['q'])
+        cc.append(graph_q['cc'])
+        pl.append(graph_q['pl'])
 
         graph_repos = set()
         for repos in [contributors[node] for node in subgraph.nodes()]:
@@ -148,6 +160,22 @@ def graph(name, contributors_projects, popularity):
     create_histogram(name + "-q", q, log_y_scale=True)
     create_histogram(name + "-smallworld", [x for x in small_worldness if x is not None and x < 10])
     highest_performing(name, bins, values)
+
+    write_table("subgraphs_summary",
+                table.create_table("Summary", "Summary", len(subgraphs),
+                                   {
+                                       "Q": q,
+                                       "CC": cc,
+                                       "PL": pl,
+                                       "Popularity": popularity_score,
+                                       "Small World": [x for x in small_worldness if x is not None],
[…]

### 2013-11-08 paper/main.tex
Added tables.

@@
 \section{Introduction}
+A social network is a graph people and the interactions between them.
+The dynamics of social networks have proved to be an important research topic for many different areas of study, from academic publication\cite{barabasi2002evolution}, to the success of broadway musicals\cite{uzzi2005collaboration}.
+In general, a social network is important to understanding how ideas and influence are spread\cite{kempe2003maximizing}, from which we can investigate the best conditions for optimal group perfomance within these networks.
 
-\subsection{Hypotheses}
+A `small world' network is a social network characterized by high clustering of graph nodes paired with a short average path between nodes \cite{watts1998collective}.
+Milgram, in is seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}.
+From these observations, hypotheses can be made as to the efficiency of how knowledge is transfered in these groups\cite{latora2001efficient}.
+In this work, we investigate the `small world' phenomenon and how it relates to Open Source Project Teams.
+
+\subsection{Hypothesis}
+
+\textit{Open Source Project Teams will perform best at moderate levels of $Q$.
+This performance, measured by the number of interest their projects generate, will increase as the level of $Q$ increases for the developer graph.
+This will continue up to an optimal $Q$ value, after which performance will begin to degrade.
+Thus, the performance curve given $Q$ will be U-shaped, and match Uzzi's findings\cite{uzzi2005collaboration}.
+}
 
 \section{Methods}
+
+We calcluate the \textit{Clustering Coefficient} (or $CC$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
+\[cc = 3 \times \frac{\text{number of triangles}}
+                    {\text{number of connected triples}}\]
+
+Also, measuring \textit{Path Length} ($PL$) allows us to gauge how far removed developers in the graph are from one another. For example
+
 \subsection{Collection and Storage}
@@
 \subsection{Quantitative}
+
+\input{tables/subgraphs_summary}
 

### 2013-11-08 code/table.py

@@ -1,0 +1,26 @@
+import numpy as np
+from collections import OrderedDict
+
+summary_functions = OrderedDict(
+    [("Mean", lambda x : round(np.mean(x),3)),
+     ("Median", lambda x : round(np.median(x),3)),
+     ("Max", lambda x : round(np.max(x),3)),
+     ("Min", lambda x : round(np.min(x),3)),
+     ("Std", lambda x : round(np.std(x),3))]
+)
+
+def create_table(title,label,N,stats,functions=summary_functions):
+    table = ""
+    table += "\\begin{table}[htbp]\centering\n"
+    table += "\caption{\label{"+label+"}\n"
+    table += "\\textbf{Statistics} }\\begin{tabular} {@{} l r "+ "".join(" r " for _ in range(len(functions))) +" @{}} \\\ \hline\n"
+    table += "\\textbf{Statistic} & " + " & ".join(["\\textbf{%s}" % key for key in functions.keys()]) + " \\\ \n"
+    table += "\hline\n"
+    table += "".join([s + " & " + " & ".join([str(f(stats[s])) for k,f in functions.items()]) + " \\\ \n" for s in stats])
+    table += "\hline\n"
+    table += "\multicolumn{"+str(len(functions)+1)+"}{@{}l}{\n"
+    table += "N = "+str(N)+"}\n"
+    table += "\end{tabular}\n"
+    table += "\end{table}\n"
+
+    return table

### 2013-11-09 code/analyze_graph.py
Swapped in the freecode data.

@@ -7,6 +7,48 @@ import numpy as np
 import math
 import table
 
+def read_contributors():
+    contributors = {}
+
+    fp = file('../data/fcProjectAuthors2013-Sep.txt')
+    csvreader = csv.DictReader(filter(lambda row: row[0]!='#', fp), delimiter='\t')
+    for row in csvreader:
+        contributor = row['author_name'].strip()
+        project = row['project_id'].strip()
+        if contributor not in contributors:
+            contributors[contributor] = []
+
+        contributors[contributor].append(project)
+    fp.close()
+
+    return contributors
+
+
+def read_stats():
+    popularity = {}
+
+    fp = file('../data/fcProjectStats2013-Sep.txt')
+    csvreader = csv.DictReader(filter(lambda row: row[0]!='#', fp), delimiter='\t')
+    for row in csvreader:
+        project_id = row['project_id'].strip()
+        popularity_score = row['popularity_score'].strip()
+        vitality_score = row['vitality_score'].strip()
+        subscriptions = row['subscriptions'].strip()
+        rank = row['popularity_rank'].strip()
+
+        score = 0
+        try:
+            score = float(popularity_score)
+        except ValueError, e:
+            print "ERROR calculating project score: %s" % str(popularity_score)
+            score = 0
+
+        if project_id not in popularity: popularity[project_id] = score
+
+    fp.close()
+
+    return popularity
+
 def read_github():
     contributors = {}
     projects = {}
@@ -84,21 +126,16 @@ def compute_random_graph(nodes, edges):
     return graph_r
 
 
-def graph(name, contributors_projects, popularity):
-
-    contributors = contributors_projects[0]
-    projects = contributors_projects[1]
-
+def graph(name, contributors, popularity):
     G = nx.Graph()
 
-    for project in projects:
-        project_contributors = projects[project]
-        if len(project_contributors) == 1:
-            G.add_node(project_contributors[0])
-        else:
-            for combination in itertools.combinations(projects[project], r=2):
-                e0 = combination[0]
-                e1 = combination[1]
+    for contributor in contributors:
+        contributor_projects = contributors[contributor]
+
+        for combination in itertools.combinations(contributor_projects, r=2):
+            e0 = combination[0]
+            e1 = combination[1]
[…]

### 2013-11-13 paper/main.tex
Updated main.
Swapped in the freecode data.
Progress... added a few more images.

@@
 \usepackage{mathrsfs}
+\usepackage{tikz}
 
@@
 
-We calcluate the \textit{Clustering Coefficient} (or $CC$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
-\[cc = 3 \times \frac{\text{number of triangles}}
+\subsection{Collection and Storage}
+Data was collected using the freely available FLOSSmole\cite{floss2006} data sets of free and open source projects.
+The data collection used was collected from the popular open source project site FreeCode\footnote{http://freecode.com/}, and contains data up to September, 2013.
+
+\subsection{Analysis}
+Results were analyzed using the Python graph processing packaged NetworkX\cite{hagberg-2008-exploring}.
+
+We calcluate the \textit{Clustering Coefficient} (or $C^\delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
+\[C^\delta = 3 \times \frac{\text{number of triangles}}
                     {\text{number of connected triples}}\]
 
-Also, measuring \textit{Path Length} ($PL$) allows us to gauge how far removed developers in the graph are from one another. For example
+Also, measuring \textit{Path Length} ($L$) allows us to gauge how far removed developers in the graph are from one another. For example
 
-\subsection{Collection and Storage}
+\begin{tikzpicture}
+  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
+  \node (n1) at (15,8) {1};
+  \node (n2) at (12,6)  {2};
+  \node (n3) at (9,5)  {3};
+  \node (n4) at (6,5)  {4};
 
-\subsection{Analysis}
+  \draw ({n1}) -- ({n2});
+  \draw ({n2}) -- ({n3});
+  \draw ({n3}) -- ({n4});
+\end{tikzpicture}
+
+\begin{tikzpicture}
+  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
+  \node (n1) at (15,8) {1};
+  \node (n2) at (12,5)  {2};
+  \node (n3) at (9,5)  {3};
+  \node (n4) at (11,8)  {4};
+
+  \draw ({n1}) -- ({n2});
+  \draw ({n2}) -- ({n3});
+  \draw ({n3}) -- ({n4});
+  \draw ({n1}) -- ({n4});
+  \draw ({n1}) -- ({n3});
+  \draw ({n2}) -- ({n4});
+\end{tikzpicture}
+
+\begin{tikzpicture}
+  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
+  \node (n1) at (15,7) {1};
+  \node (n2) at (12,5)  {2};
+  \node (n3) at (8,7)  {3};
+  \node (n4) at (11,8)  {4};
+
+  \draw ({n1}) -- ({n2});
+  \draw ({n3}) -- ({n4});
+  \draw ({n1}) -- ({n4});
+  \draw ({n2}) -- ({n4});
+\end{tikzpicture}
+
+\textit{Small-World-ness}
+
+\[\gamma^{\Delta}_g = \frac{C^{\Delta}_g }{C^{\Delta}_{rand} } \]
+
+\[\lambda_g = \frac{L_g }{L_{rand} } \]
+
+\[S^\Delta = \frac{\gamma^{\Delta}_g }{\lambda_g} \]
 
@@
 \input{tables/subgraphs_summary}
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{images/freecode-popular.png}
+\end{center}
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{images/freecode-unpopular.png}
+\end{center}
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{images/freecode-q-histo.png}
+\end{center}
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{images/freecode-smallworld-histo.png}
+\end{center}
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{images/freecode-graph.png}
+\end{center}
 

### 2013-11-13 code/analyze_graph.py

@@ -32,11 +32,7 @@ def read_stats():
     for row in csvreader:
         project_id = row['project_id'].strip()
         popularity_score = row['popularity_score'].strip()
-        vitality_score = row['vitality_score'].strip()
-        subscriptions = row['subscriptions'].strip()
-        rank = row['popularity_rank'].strip()
 
-        score = 0
         try:
             score = float(popularity_score)
         except ValueError, e:
@@ -200,10 +196,10 @@ def graph(name, contributors, popularity):
                 table.create_table("Summary", "Summary", N,
                                    {
                                        "Q": q,
-                                       "CC": cc,
-                                       "PL": pl,
+                                       "$C^\Delta$": cc,
+                                       "L": pl,
                                        "Popularity": popularity_score,
-                                       "Small World": [x for x in small_worldness if x is not None],
+                                       "$S^\Delta$": [x for x in small_worldness if x is not None],
                                        "Nodes": subgraph_node_number,
                                        "Edges": subgraph_edge_number
                                    }))
@@ -240,7 +236,6 @@ def highest_performing(filename, bins, values):
         plt.hist(data, len(bins), color="0.75")
         F = plt.gcf()
         F.savefig("../paper/images/"+filename+"-"+name+".png")
-        plt.show()
         plt.close(fig)
 
 def create_graph(filename, x, y):
@@ -248,8 +243,8 @@ def create_graph(filename, x, y):
     median = [np.median(j) for j in y]
 
     fig = plt.figure()
-    plt.plot(x,avg,'bo')
-    plt.plot(x,median,'ro')
+    plt.plot(x,avg,'b-')
+    plt.plot(x,median,'r-')
     F = plt.gcf()
     F.savefig("../paper/images/"+filename+"-graph.png")
     plt.close(fig)

### 2013-11-13 code/table.py

@@ -1,12 +1,14 @@
 import numpy as np
 from collections import OrderedDict
 
+sigdigits = 2
+
 summary_functions = OrderedDict(
-    [("Mean", lambda x : round(np.mean(x),3)),
-     ("Median", lambda x : round(np.median(x),3)),
-     ("Max", lambda x : round(np.max(x),3)),
-     ("Min", lambda x : round(np.min(x),3)),
-     ("Std", lambda x : round(np.std(x),3))]
+    [("Mean", lambda x : round(np.mean(x),sigdigits)),
+     ("Med", lambda x : round(np.median(x),sigdigits)),
+     ("Max", lambda x : round(np.max(x),sigdigits)),
+     ("Min", lambda x : round(np.min(x),sigdigits)),
+     ("Std", lambda x : round(np.std(x),sigdigits))]
 )
 
 def create_table(title,label,N,stats,functions=summary_functions):

### 2013-11-14 paper/main.tex
More paper progress.

@@
 \usepackage{tikz}
+\usetikzlibrary{positioning}
+\setlength{\abovecaptionskip}{2pt}
 
@@
 
+\textit{Graph Structure}
+A bipartite graph is a specialized type of graph containing two disjoint sets of verticies.
+This can be denoted by $G=(P,C,E)$, where $P \cap C = \emptyset$.
+For our purposes, let set $P$ be the set of all projects, and set $C$ be the set of all contributors.
+Each project node, therefore, is only connected to contributor nodes, and vice versa.
+
+\begin{figure}
+\label{fig:example_graphs}
+\centering
+\begin{tikzpicture}
+\tikzset{P/.style={circle,fill=lightgray!20}}
+\tikzset{C/.style={circle,fill=black!20}}
+
+ [scale=.5,auto=left]
+  \node[P] (p1) at (-5,3)  {$P_1$};
+  \node[P] (p2) at (-5,2)  {$P_2$};
+  \node[P] (p3) at (-5,1)  {$P_3$};
+  \node[P] (p4) at (-5,0)  {$P_4$};
+
+  \node[C] (c1) at (-2,3)  {$C_1$};
+  \node[C] (c2) at (-2,2)  {$C_2$};
+  \node[C] (c3) at (-2,1)  {$C_3$};
+  \node[C] (c4) at (-2,0)  {$C_4$};
+
+  \draw ({p1}) -- ({c1});
+  \draw ({p1}) -- ({c2});
+  \draw ({p2}) -- ({c2});
+  \draw ({p2}) -- ({c4});
+  \draw ({p3}) -- ({c3});
+  \draw ({p4}) -- ({c3});
+  \node[draw=none,fill=none,rectangle,left=1mm of p1] {Projects}; 
+  \node[draw=none,fill=none,rectangle,right=1mm of c1] {Contributors}; 
+\end{tikzpicture}
+\caption{A caption.}
+\end{figure}
+
+This is a typical representation found in social and collaboration networks\cite{ramasco2004self}.
+
+The collected data was organized into a graph structure $G$, with the nodes representing the projects and the edges representing one or more shared developer between projects.
+
 We calcluate the \textit{Clustering Coefficient} (or $C^\delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
@@
 
-Also, measuring \textit{Path Length} ($L$) allows us to gauge how far removed developers in the graph are from one another. For example
+Also, measuring \textit{Path Length} ($L$) allows us to determine how far removed developers in the graph are from one another. For example
 
+\begin{figure}
+\label{fig:example_graphs}
+\centering
 \begin{tikzpicture}
@@
   \node (n4) at (6,5)  {4};
+  \node[draw=none,fill=none,rectangle,right=1mm of n1] {$C^\Delta = 0.0$};
 
@@
   [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
+
   \node (n1) at (15,8) {1};
@@
   \node (n4) at (11,8)  {4};
+  \node[draw=none,fill=none,rectangle,right=1mm of n1] {$C^\Delta = 1.0$};
 
@@
   \node (n4) at (11,8)  {4};
+  \node[draw=none,fill=none,rectangle,right=1mm of n1] {$C^\Delta = 0.6$};
 
@@
 \end{tikzpicture}
+\caption{A caption.}
+\end{figure}
 
@@
 
+Summary statistics for the graph analysis are captured in figure \ref{fig:summary_stats}.
+First, $S^\Delta > 1$ is observed for both the mean and the median, which meets the criteria for a small-world network\cite{humphries2008network}.\\
+
+$Q$ and $C^\Delta$ both indicate a non-normal distribution, as shown by the large standard deviation.
+This observation indicates a propensity towards the extremes of these measurements.
+This is further reinforced by the distribution of $Q$ shown in figure \ref{fig:q_distribution}.
+This figure indicates that the majority of subgraphs have a $Q$ and $C^\Delta$ value of either 0 or 1.\\
+
+Exploring this phenomenon further, follows that most graphs resemble the top or the middle graph in figure \ref{fig:example_graphs}, with relatively few resembling the bottom graph.
+
+\begin{figure}
+\label{fig:cc_popular}
 \begin{center}
+\caption{$C^\Delta$ of Popular Projects}
 \includegraphics[width=0.5\textwidth]{images/freecode-popular.png}
 \end{center}
+\end{figure}
 
+\begin{figure}
 \begin{center}
+\caption{$C^\Delta$ of Unpopular Projects}
 \includegraphics[width=0.5\textwidth]{images/freecode-unpopular.png}
 \end{center}
+\end{figure}
 
+\begin{figure}
+\label{fig:q_distribution}
 \begin{center}
+\caption{$Q$ Distribution}
 \includegraphics[width=0.5\textwidth]{images/freecode-q-histo.png}
 \end{center}
+\end{figure}
 
+\begin{figure}
 \begin{center}
+\caption{$S^\Delta$ Distribution}
 \includegraphics[width=0.5\textwidth]{images/freecode-smallworld-histo.png}
 \end{center}
+\end{figure}
 
+\begin{figure}
 \begin{center}
+\caption{$C^\Delta$ and Project Popularity}
 \includegraphics[width=0.5\textwidth]{images/freecode-graph.png}
 \end{center}
+\end{figure}
+
+The project graph contains a large amount of subgraphs, and as a whole appears less clustered than some other observed social network graphs\cite{madey2002open}.
 
@@
 \section{Conclusion}
+
 \section{Acknowledgments}

### 2013-11-14 code/analyze_graph.py

@@ -4,7 +4,6 @@ import itertools
 import matplotlib.pyplot as plt
 import random
 import numpy as np
-import math
 import table
 
 def read_contributors():
@@ -45,29 +44,6 @@ def read_stats():
 
     return popularity
 
-def read_github():
-    contributors = {}
-    projects = {}
-    popularity = {}
-    csvreader = csv.DictReader(open('../data/combined.csv'), delimiter=',')
-    for row in csvreader:
-        if row['repository_fork'] == 'true':
-            continue
-
-        forks = int(row['repository_forks'])
-        watchers = int(row['repository_watchers'])
-        project = row['repository_url']
-        popularity[project] = int(math.sqrt(forks * watchers))
-        contributor = row['actor_attributes_login']
-        if contributor not in contributors:
-            contributors[contributor] = []
-        if project not in projects:
-            projects[project] = []
-
-        contributors[contributor].append(project)
-        projects[project].append(contributor)
-
-    return contributors, projects, popularity
 
 def reject_outliers(data):
     return data
@@ -192,8 +168,10 @@ def graph(name, contributors, popularity):
     create_histogram(name + "-smallworld", [x for x in small_worldness if x is not None])
     highest_performing(name, bins, values)
 
+    total_projects = len(set(sum(contributors.values(), [])))
+
     write_table("subgraphs_summary",
-                table.create_table("Summary", "Summary", N,
+                table.create_table("Summary", "fig:summary_stats", "Projects: %s, Subgraphs: %s, Contributors: %s" % (total_projects, N, len(contributors.keys())),
                                    {
                                        "Q": q,
                                        "$C^\Delta$": cc,

### 2013-11-14 code/table.py

@@ -11,7 +11,7 @@ summary_functions = OrderedDict(
      ("Std", lambda x : round(np.std(x),sigdigits))]
 )
 
-def create_table(title,label,N,stats,functions=summary_functions):
+def create_table(title,label,caption,stats,functions=summary_functions):
     table = ""
     table += "\\begin{table}[htbp]\centering\n"
     table += "\caption{\label{"+label+"}\n"
@@ -21,7 +21,7 @@ def create_table(title,label,N,stats,functions=summary_functions):
     table += "".join([s + " & " + " & ".join([str(f(stats[s])) for k,f in functions.items()]) + " \\\ \n" for s in stats])
     table += "\hline\n"
     table += "\multicolumn{"+str(len(functions)+1)+"}{@{}l}{\n"
-    table += "N = "+str(N)+"}\n"
+    table += caption+"}\n"
     table += "\end{tabular}\n"
     table += "\end{table}\n"
 

### 2013-11-14 paper/main.tex
Added to the analysis.

@@
 \subsection{Analysis}
-Results were analyzed using the Python graph processing packaged NetworkX\cite{hagberg-2008-exploring}.
+The collected data was organized into a graph structure, with the nodes representing the projects and the edges representing one or more shared developer between projects.
 
@@
 A bipartite graph is a specialized type of graph containing two disjoint sets of verticies.
-This can be denoted by $G=(P,C,E)$, where $P \cap C = \emptyset$.
+This can be denoted by ${G=(P,C,E)}$, where ${P \cap C = \emptyset}$.
 For our purposes, let set $P$ be the set of all projects, and set $C$ be the set of all contributors.
-Each project node, therefore, is only connected to contributor nodes, and vice versa.
+Each project node, therefore, is only connected to contributor nodes, and vice versa, as show in figure \ref{fig:example_bipartite_graph}.
+This bipartite representation is typical of what is found in social and collaboration networks\cite{ramasco2004self}.
 
 \begin{figure}
-\label{fig:example_graphs}
+\label{fig:example_bipartite_graph}
 \centering
@@
   \draw ({p1}) -- ({c2});
-  \draw ({p2}) -- ({c2});
-  \draw ({p2}) -- ({c4});
+  \draw ({p2}) -- ({c2});;
+  \draw ({p3}) -- ({c2});
   \draw ({p3}) -- ({c3});
   \draw ({p4}) -- ({c3});
+  \draw ({p4}) -- ({c4});
   \node[draw=none,fill=none,rectangle,left=1mm of p1] {Projects}; 
@@
 \end{tikzpicture}
-\caption{A caption.}
+\caption{An example bipartite graph of Projects and Contributors}
 \end{figure}
 
-This is a typical representation found in social and collaboration networks\cite{ramasco2004self}.
+A bipartite graph projection.
+in necessary to further analyze the graph.
+A bipartite projection involves taking the disjoint node sets $P$ and $C$, and representing the graph as relationships between only one of those sets of nodes.
+A projection onto the project nodes, or $P$, of figure \ref{fig:example_bipartite_graph} is show in figure \ref{fig:example_bipartite_projection_graph}.
+Here, projects are connected directly, with edges occurring if one or more developer is shared between the projects.
+It is important to note that the projection could have been done in terms of the contributors, not the projects.
+This would have led to a graph with nodes of contributors $C$, each being linked by sharing a common project.
+This approach is another common way of representing these bipartite graphs\cite{newman2001scientific}, and illustrates the fact that a bipartite projections are lossy compared to the data reprented in the original graph\cite{zhou2007bipartite}.\\
 
-The collected data was organized into a graph structure $G$, with the nodes representing the projects and the edges representing one or more shared developer between projects.
+One of the main sources of information loss is multiple connections between projects, or projects that share multiple collaborators.
+When doing a bipartite projection based on projects $P$, a single link could represent one shared developer or many.
+This is an evident source of data loss in the projection.
+The simple approach is to treat one connection the same as many connections between nodes.
+This is straightforward but lossy\cite{zhou2007bipartite,grossman1995portion}.
+A better approach is to assign a \textit{weight} to each edge representing repeated links -- or in our case -- multiple shared collaborators\cite{zha2001bipartite}.
 
-We calcluate the \textit{Clustering Coefficient} (or $C^\delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
+\begin{figure}
+\label{fig:example_bipartite_projection_graph}
+\centering
+\begin{tikzpicture}
+\tikzset{P/.style={circle,fill=lightgray!20}}
+\tikzset{C/.style={circle,fill=black!20}}
+
+ [scale=.5,auto=left]
+  \node[P] (p1) at (-5,3)  {$P_1$};
+  \node[P] (p2) at (-3,2)  {$P_2$};
+  \node[P] (p3) at (-5,1)  {$P_3$};
+  \node[P] (p4) at (-2,1)  {$P_4$};
+
+  \draw ({p1}) -- ({p3});
+  \draw ({p1}) -- ({p2});
+  \draw ({p1}) -- ({p2});
+  \draw ({p2}) -- ({p3});
+  \draw ({p3}) -- ({p4});
+\end{tikzpicture}
+\caption{A $P$ projection of the figure \ref{fig:example_bipartite_graph} bipartite graph}
+\end{figure}
+
+We calcluate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
 \[C^\delta = 3 \times \frac{\text{number of triangles}}
@@
 Also, measuring \textit{Path Length} ($L$) allows us to determine how far removed developers in the graph are from one another. For example
+
+Results were analyzed using the Python graph processing packaged NetworkX\cite{hagberg-2008-exploring}.
 

### 2013-11-14 code/analyze_graph.py

@@ -68,8 +68,9 @@ def get_small_worldness(q_dict_g, q_dict_rand):
 def compute_q(graph):
     cc = nx.transitivity(graph)
     pl = nx.average_shortest_path_length(graph)
+    avg_cc = nx.average_clustering(graph, weight="weight")
 
-    return {"q":cc/pl,"pl":pl,"cc":cc}
+    return {"q":cc/pl,"pl":pl,"cc":cc, "avg_cc": avg_cc}
 
 def compute_random_graph(nodes, edges):
 
@@ -108,11 +109,14 @@ def graph(name, contributors, popularity):
             e0 = combination[0]
             e1 = combination[1]
             if not G.has_edge(e0,e1) and not G.has_edge(e1,e0):
-                G.add_edge(e0,e1)
+                G.add_edge(e0,e1, weight=1)
+            else:
+                G[e0][e1]['weight'] += 1
 
     q = []
     cc = []
     pl = []
+    avg_cc = []
     popularity_score = []
     small_worldness = []
     subgraph_node_number = []
@@ -143,6 +147,7 @@ def graph(name, contributors, popularity):
         q.append(graph_q['q'])
         cc.append(graph_q['cc'])
         pl.append(graph_q['pl'])
+        avg_cc.append(graph_q['avg_cc'])
 
         try:
             avg_popularity = np.mean([float(popularity[node]) for node in subgraph])
@@ -175,6 +180,7 @@ def graph(name, contributors, popularity):
                                    {
                                        "Q": q,
                                        "$C^\Delta$": cc,
+                                       "$\overline{C^\Delta}$": avg_cc,
                                        "L": pl,
                                        "Popularity": popularity_score,
                                        "$S^\Delta$": [x for x in small_worldness if x is not None],

### 2013-11-16 paper/main.tex
A few more references.

@@
 \setlength{\abovecaptionskip}{2pt}
+\setcounter{secnumdepth}{2}
 
@@
 
-\textit{Graph Structure}
+\subsubsection{Graph Structure}
 A bipartite graph is a specialized type of graph containing two disjoint sets of verticies.
@@
 When doing a bipartite projection based on projects $P$, a single link could represent one shared developer or many.
-This is an evident source of data loss in the projection.
+This is a source of data loss in the projection.
 The simple approach is to treat one connection the same as many connections between nodes.
 This is straightforward but lossy\cite{zhou2007bipartite,grossman1995portion}.
-A better approach is to assign a \textit{weight} to each edge representing repeated links -- or in our case -- multiple shared collaborators\cite{zha2001bipartite}.
+A better approach is to assign a \textit{weight} to each edge representing repeated links -- or in our case -- multiple shared collaborators\cite{zha2001bipartite,barrat2004architecture}.
 
@@
 
-We calcluate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
+\subsubsection{Graph Analysis}
+To support our hypotheses, there are several key metrics to be studied in regards to the aforementioned graph.
+Many of these metrics follow the work of Boccaletti \textit{et.
+al}\cite{boccaletti2006complex}, and other studies of similar graph types CITATION HERE.
+
+\textit{Clustering Coefficient (Transitivity}\\
+We calculate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
 \[C^\delta = 3 \times \frac{\text{number of triangles}}
@@
 
-Also, measuring \textit{Path Length} ($L$) allows us to determine how far removed developers in the graph are from one another. For example
+\textit{Clustering Coefficient (Average}\\
+Another approach to clustering is to take the average of each node's local clustering coefficient\cite{watts1998collective}.
+
+\[ c_i = \frac{|\{e_{jk}\}|}{k_i(k_i-1)} :\, v_j,v_k \in N_i,\, e_{jk} \in E \]
+
+{$N_i = \{v_j : e_{ij} \in E\}$}
+
+\textit{Average Path Length}\\
+Also, calculating the \textit{Path Length} ($L$) allows us to determine how far removed developers in the graph are from one another.
+The path length is calculated as the average distance between any two node pairs in the graph:
+
+\[L = \frac{1}{|P| \cdot (|P|-1)} \sum_{i \neq j}\lambda(v_i,v_j)\]
+
+Where {$v_i \in P$}, {$v_j \in P$}, and {$\lambda(v_i,v_j)$} denotes the shortest path between the two nodes.
+We only consider path length for connected subgraphs, avoiding some complexities of this calculation on disconnected graphs\cite{boccaletti2006complex}.
 
@@
 
-\textit{Small-World-ness}
+\textit{Small-World-ness}\\
 
@@
 \[S^\Delta = \frac{\gamma^{\Delta}_g }{\lambda_g} \]
+
+\subsubsection{Qualitative Analysis}
+It has been well recognized through history that people tend to make connections with people with whom they share similarities\cite{mcpherson2001birds}.
 

### 2013-11-16 paper/main.tex
A little more analysis.

@@
 
-\textit{Clustering Coefficient (Transitivity}\\
+\textit{Clustering Coefficient (Transitivity)}\\
 We calculate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
@@
 
-\textit{Clustering Coefficient (Average}\\
+\textit{Clustering Coefficient (Average)}\\
 Another approach to clustering is to take the average of each node's local clustering coefficient\cite{watts1998collective}.
@@
 This is further reinforced by the distribution of $Q$ shown in figure \ref{fig:q_distribution}.
-This figure indicates that the majority of subgraphs have a $Q$ and $C^\Delta$ value of either 0 or 1.\\
+This figure indicates that the majority of subgraphs have a $Q$ and $C^\Delta$ value of close to either 0 or 1.\\
 
 Exploring this phenomenon further, follows that most graphs resemble the top or the middle graph in figure \ref{fig:example_graphs}, with relatively few resembling the bottom graph.
+
+To validate the hypothesis, we expect to find that medium values of $C^\Delta$ will be correlated with more popular projects.
+To explore this possibility, we first compare the popularity given $C^\Delta$ values as shown in figure \ref{fig:cc_popular}.
+The $C^\Delta$ values do display the U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi \textit{et.
+al}\cite{uzzi2005collaboration}.
+It is important to note, however that, the standard deviation is high, as shown in both \ref{fig:summary_stats} and the significant difference between the mean and median results.
 

### 2013-11-17 paper/main.tex
A little more analysis.

@@
 \subsubsection{Qualitative Analysis}
-It has been well recognized through history that people tend to make connections with people with whom they share similarities\cite{mcpherson2001birds}.
+It has been asserted that people tend to make connections with people with whom they share similarities\cite{mcpherson2001birds}.
+This idea of homophily, however, needs to be further expanded before we can make assertions about correlations to performance.
+It has been shown that demographic homophily is complex to measure, correlates little to performance outcomes, and in fact correlate negatively\cite{reagans2004make,lawrence1997perspective}.
+For our purposes, it is much more appropriate to examine how teams best leverage similarities of knowledge and information, as the flow of these assets can be a key driver to success\cite{nissen2002extended}.
 

### 2013-11-18 paper/main.tex
Fixed bad reference links.

@@
 \begin{figure}
-\label{fig:example_bipartite_graph}
 \centering
@@
 \caption{An example bipartite graph of Projects and Contributors}
+\label{fig:example_bipartite_graph}
 \end{figure}
@@
 \begin{figure}
-\label{fig:example_bipartite_projection_graph}
 \centering
@@
 \caption{A $P$ projection of the figure \ref{fig:example_bipartite_graph} bipartite graph}
+\label{fig:example_bipartite_projection_graph}
 \end{figure}
@@
 \begin{figure}
-\label{fig:example_graphs}
 \centering
@@
 \caption{A caption.}
+\label{fig:example_graphs}
 \end{figure}
@@
 \textit{Small-World-ness}\\
+The idea of a \textit{small world} can be formalized by the following equations\cite{humphries2008network}.
 
+First, let $\gamma^{\Delta}_g$ equal the ratio of the clustering coefficient of a given graph and a random graph.
 \[\gamma^{\Delta}_g = \frac{C^{\Delta}_g }{C^{\Delta}_{rand} } \]
 
+Next apply a similar pattern to the average path length $\lambda_g$.
 \[\lambda_g = \frac{L_g }{L_{rand} } \]
 
+Finally, the ratio of the above calculations yields the small-world-ness, or $S^\Delta$, of the graph
 \[S^\Delta = \frac{\gamma^{\Delta}_g }{\lambda_g} \]
+
+We assume for throughout that any graph exhibiting $S^\Delta > 1$ is a small-world graph.
+
+\textit{Successful vs Unsuccessful}\\
+To further explore the data, a comparion was made between \textit{successful} and \textit{unsuccessful} projects was made.
+We define \textit{successful} as any project with {$PopularityScore > 100$}, and \textit{unsuccessful} as any project with {$PopularityScore < 50$}.
+Given this view of the data, we can then make assertions about how we expect these types of projects to behave, given the stated hypothesis.
+More specifically, we can examine not only if the u-shaped curve holds for \textit{popular} projects, but if the inverse holds for \textit{unsuccessful} ones.
 
@@
 To validate the hypothesis, we expect to find that medium values of $C^\Delta$ will be correlated with more popular projects.
-To explore this possibility, we first compare the popularity given $C^\Delta$ values as shown in figure \ref{fig:cc_popular}.
+To explore this possibility, we first compare the popularity given $C^\Delta$ values as shown in figure \ref{fig:cc_graph}.
 The $C^\Delta$ values do display the U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi \textit{et.
@@
 \begin{figure}
-\label{fig:cc_popular}
+\begin{center}
+\caption{$C^\Delta$ and Project Popularity}
+\includegraphics[width=0.5\textwidth]{images/freecode-graph.png}
+\end{center}
+\caption{A caption.}
+\label{fig:cc_graph}
+\end{figure}
+
+Popular projects do appear to conform to the results found by Uzzi\cite{uzzi2005collaboration}.
+As show in figure \ref{fig:cc_unpopular}, $C^\Delta$ near the extremes (0.0 or 1.0) show a relatively low likelihood of being popular.
+As $C^\Delta$ values approach mid-range values, the probability of a project being a success increases greatly.
+
+\begin{figure}
 \begin{center}
@@
 \end{center}
+\caption{A caption.}
+\label{fig:cc_popular}
 \end{figure}
+
+The inverse is true of unpopular projects.
+As $C^\Delta$ near the extremes (0.0 or 1.0), a high probability of being unsuccessful is observed.
+Mid-valued $C^\Delta$ values indicate a substantially lower probability of being unsuccessful.
 
@@
 \end{center}
+\caption{A caption.}
+\label{fig:cc_unpopular}
 \end{figure}
@@
 \begin{figure}
-\label{fig:q_distribution}
 \begin{center}
@@
 \end{center}
+\caption{A caption.}
+\label{fig:q_distribution}
 \end{figure}
@@
 \end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\caption{$C^\Delta$ and Project Popularity}
-\includegraphics[width=0.5\textwidth]{images/freecode-graph.png}
-\end{center}
+\caption{A caption.}
+\label{fig:sw_distribution}
 \end{figure}
@@
 
+A futher area of study would be how this relates to previously defined \textit{success factors} in projects\cite{cooke2002real}.
+
 \section{Acknowledgments}

### 2013-11-19 paper/main.tex
Added interview questions.

@@
 \title{
-The Small World Network Effect in Open Source Project Teams
+The Small World Network Effect in Software Project Teams
 \author{Kevin Peterson\\
@@
 
-\noindent \\\textbf{Keywords.} Git, GitHub, Open Source
+\noindent \\\textbf{Keywords.} Small World, Project Management, Software
 
@@
 A `small world' network is a social network characterized by high clustering of graph nodes paired with a short average path between nodes \cite{watts1998collective}.
-Milgram, in is seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}.
+`Clustering' in this context means how closely nodes in the graph are related to each other, or "the friend of my friend is also my friend." Milgram, in is seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}.
 From these observations, hypotheses can be made as to the efficiency of how knowledge is transfered in these groups\cite{latora2001efficient}.
-In this work, we investigate the `small world' phenomenon and how it relates to Open Source Project Teams.
+In this work, we investigate the `small world' phenomenon and how it relates to Software Project Teams.
 
 \subsection{Hypothesis}
+The formalization of the `small world' quality of a graph can be expressed by the \textit{Small World Quotient}, or $Q$\cite{watts1999small,watts1998collective}.
+The value $Q$ is calculated by dividing the clustering factor of graph by the average path length between nodes.
+Uzzi explored this value in graphs of Broadway productions\cite{uzzi2005collaboration}.
+His findings suggest that the success of Broadway productions is greatest when teams have a good mix of new and familiar members.
+Productions are less likely to be successful when team members are very familiar with each other.
+Also, probability of success drops much the same way when there is little familiarity between team members.
+This indicates that there is an optimal ratio of new and familiar members on a team -- or, an optimal value of $Q$ when related to performance.
 
-\textit{Open Source Project Teams will perform best at moderate levels of $Q$.
+\textit{Software Project Teams will perform best at moderate levels of $Q$.
 This performance, measured by the number of interest their projects generate, will increase as the level of $Q$ increases for the developer graph.
 This will continue up to an optimal $Q$ value, after which performance will begin to degrade.
-Thus, the performance curve given $Q$ will be U-shaped, and match Uzzi's findings\cite{uzzi2005collaboration}.
-}
+Thus, the performance curve given $Q$ will be U-shaped, and match Uzzi's findings\cite{uzzi2005collaboration}.}
 
@@
 The data collection used was collected from the popular open source project site FreeCode\footnote{http://freecode.com/}, and contains data up to September, 2013.
+Results were analyzed using the Python graph processing packaged NetworkX\cite{hagberg-2008-exploring}.
+All source code pertaining to the collection and analysis can be found at \url{https://github.com/kevinpeterson/small-world-effect-research}.
 
@@
 The collected data was organized into a graph structure, with the nodes representing the projects and the edges representing one or more shared developer between projects.
+Various properties of the graph are analyzied, as indicated in the sections below.
 
 \subsubsection{Graph Structure}
-A bipartite graph is a specialized type of graph containing two disjoint sets of verticies.
-This can be denoted by ${G=(P,C,E)}$, where ${P \cap C = \emptyset}$.
-For our purposes, let set $P$ be the set of all projects, and set $C$ be the set of all contributors.
-Each project node, therefore, is only connected to contributor nodes, and vice versa, as show in figure \ref{fig:example_bipartite_graph}.
-This bipartite representation is typical of what is found in social and collaboration networks\cite{ramasco2004self}.
+We first consider the FreeCode FLOSSmole\cite{floss2006} data sets to be one large graph.
+From this large disconnected graph, each connected subgraph is analyzed.
+Metrics are computed for each of these subgraphs, and a total subgraph performance is computed by averaging the performance value of each graph in the subgraph.
+We measure a subgraph's perfomance by the FreeCode \textit{Popularity Score} metric, which is calculated the following formula\footnote{http://help.freecode.com/kb/statistics/how-do-you-measure-a-projects-popularity}:
+
+\[ ((record\ hits + URL\ hits) \cdot (followers + 1))^{1/2} \]
 
@@
 \end{figure}
+
+A bipartite graph is a specialized type of graph containing two disjoint sets of verticies.
+This can be denoted by ${G=(P,C,E)}$, where ${P \cap C = \emptyset}$.
+For our purposes, let set $P$ be the set of all projects, and set $C$ be the set of all contributors.
+Each project node, therefore, is only connected to contributor nodes, and vice versa, as show in figure \ref{fig:example_bipartite_graph}.
+This bipartite representation is typical of what is found in social and collaboration networks\cite{ramasco2004self}.
 
@@
 Many of these metrics follow the work of Boccaletti \textit{et.
-al}\cite{boccaletti2006complex}, and other studies of similar graph types CITATION HERE.
+al}\cite{boccaletti2006complex}, and other studies of similar graph types\cite{latora2001efficient,adamic1999small}.
 
-\textit{Clustering Coefficient (Transitivity)}\\
+\noindent\\\textit{Clustering Coefficient - Transitivity ($C^\Delta$)}\\
 We calculate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
-\[C^\delta = 3 \times \frac{\text{number of triangles}}
+\[C^\Delta = 3 \times \frac{\text{number of triangles}}
                     {\text{number of connected triples}}\]
 
-\textit{Clustering Coefficient (Average)}\\
+\noindent\\\textit{Clustering Coefficient - Average ($\overline{C^\Delta}$)}\\
 Another approach to clustering is to take the average of each node's local clustering coefficient\cite{watts1998collective}.
 
-\[ c_i = \frac{|\{e_{jk}\}|}{k_i(k_i-1)} :\, v_j,v_k \in N_i,\, e_{jk} \in E \]
+\[ C_i = \frac{|\{e_{jk}\}|}{k_i(k_i-1)} :\, v_j,v_k \in N_i,\, e_{jk} \in E \]
 
@@
 
-\textit{Average Path Length}\\
+\[ \overline{C^\Delta} = \frac{1}{|P|}\sum^{|P|}_{i=1}C_i \]
+Unless otherwise noted, the Transitivity version of this metric ($C^\Delta$) will be used for all further calculations and metrics.
+
+\noindent\\\textit{Average Path Length ($L$)}\\
 Also, calculating the \textit{Path Length} ($L$) allows us to determine how far removed developers in the graph are from one another.
@@
 
-Results were analyzed using the Python graph processing packaged NetworkX\cite{hagberg-2008-exploring}.
+\noindent\\\textit{Small World Quotient ($Q$)}\\
+The \textit{Small World Quotient} ($Q$) is defined as the Clustering Coefficient ($C^\Delta$) divided by the  Average Path Length ($L$)\cite{watts1999small,watts1998collective}.
+
+\[Q =  \frac{C^\Delta}{L}\]
 
@@
 \end{tikzpicture}
-\caption{A caption.}
+\caption{Example Clustering Coefficient ($C^\Delta$) values for sample graphs}
 \label{fig:example_graphs}
@@
 
-\textit{Small-World-ness}\\
-The idea of a \textit{small world} can be formalized by the following equations\cite{humphries2008network}.
+\noindent\\\textit{Small-World-ness ($S^\Delta$)}\\
+The definition of a \textit{small world} graph can be formalized by the following equations\cite{humphries2008network}.
 
@@
 
-\textit{Successful vs Unsuccessful}\\
+\noindent\\\textit{Successful vs Unsuccessful}\\
 To further explore the data, a comparion was made between \textit{successful} and \textit{unsuccessful} projects was made.
@@
 It has been shown that demographic homophily is complex to measure, correlates little to performance outcomes, and in fact correlate negatively\cite{reagans2004make,lawrence1997perspective}.
-For our purposes, it is much more appropriate to examine how teams best leverage similarities of knowledge and information, as the flow of these assets can be a key driver to success\cite{nissen2002extended}.
+For our purposes, it is much more appropriate to examine how teams best leverage similarities of knowledge and information, as the flow of these assets can be a key driver to success\cite{nissen2002extended}.\\
+In the same way we can explore the role of team familiarity.
+The two types of familiarity that we will explore are \textit{member} familiarity and \textit{task/project} familiarity\cite{harrison2003time}.
+These metrics, although not captured in data, could be important factors in \textit{how} teams form, and thus help us to understand \textit{why} teams perform the way that they do.\\
+
+To further study these factors, we arranged interviews with two current professionals in the field.
+Both have had experience with project management and are certified Project Management Professionals (PMP)\textregistered.
+We proposed to them the following questions:
+
+\noindent\\\textit{Q1: How do development teams collaborate and share ideas?}\\
+\noindent\\\textit{Q2: Do teams generally remain intact over multiple projects, or do members often shuffle and re-combine?}\\
+\noindent\\\textit{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project.}\\
+\noindent\\\textit{Q4: What are some characteristics of a high performing team?}\\
+\noindent\\\textit{Q5: In your experience, is it better to (A) keep an innovative team intact, (B) periodically bring in new members or re-assign exising members, or (C) split up and disperse the team to as many other projects as possible?}\\
 
@@
 \begin{center}
-\caption{$C^\Delta$ and Project Popularity}
 \includegraphics[width=0.5\textwidth]{images/freecode-graph.png}
 \end{center}
-\caption{A caption.}
+\caption{$C^\Delta$ and Project Popularity}
 \label{fig:cc_graph}
@@
 \begin{center}
-\caption{$C^\Delta$ of Popular Projects}
 \includegraphics[width=0.5\textwidth]{images/freecode-popular.png}
 \end{center}
-\caption{A caption.}
+\caption{$C^\Delta$ of Popular Projects}
 \label{fig:cc_popular}
@@
 \begin{center}
-\caption{$C^\Delta$ of Unpopular Projects}
 \includegraphics[width=0.5\textwidth]{images/freecode-unpopular.png}
 \end{center}
-\caption{A caption.}
+\caption{$C^\Delta$ of Unpopular Projects}
 \label{fig:cc_unpopular}
@@
 
+Distribution of $Q$ values are shown in figure\ref{fig:q_distribution}. This indicates that the majority of sub-graphs have a $Q$ value near either 0.0 or 1.0.
+
 \begin{figure}
 \begin{center}
-\caption{$Q$ Distribution}
 \includegraphics[width=0.5\textwidth]{images/freecode-q-histo.png}
 \end{center}
-\caption{A caption.}
+\caption{$Q$ Distribution}
 \label{fig:q_distribution}
@@
 
+Small-world-ness, or $S^\Delta$, is generally between 1 and 3 for most sub-graphs.
+
 \begin{figure}
 \begin{center}
-\caption{$S^\Delta$ Distribution}
 \includegraphics[width=0.5\textwidth]{images/freecode-smallworld-histo.png}
 \end{center}
-\caption{A caption.}
+\caption{$S^\Delta$ Distribution}
 \label{fig:sw_distribution}
 \end{figure}
-
-The project graph contains a large amount of subgraphs, and as a whole appears less clustered than some other observed social network graphs\cite{madey2002open}.
 
@@
 \section{Conclusion}
+The project graph contains a large amount of subgraphs, and as a whole appears less clustered than some other observed social network graphs\cite{madey2002open}.
 

### 2013-11-20 paper/main.tex
Fixed CC equations.

@@
 
-\[ C_i = \frac{|\{e_{jk}\}|}{k_i(k_i-1)} :\, v_j,v_k \in N_i,\, e_{jk} \in E \]
+Given our graph of nodes $P$ connected by edges $E$, or ${G=(P,E)}$, for any given node we can determine its \textit{neighborhood} ($N_i$), or the set of nodes directly connected to a given node.
+\[ N_i = \{v_j : e_{ij} \in E \wedge e_{ji} \in E \wedge v_j \in P\} \]
 
-{$N_i = \{v_j : e_{ij} \in E\}$}
+Given this \textit{neighborhood}, we can then calculate how closely connected the nodes are.
+To do this, we take the number of actual connections between neighbors divided by the total possible number of connections, where $k_i$ represents the count of the neighbors of a node, or {$k_i = |N_i|$}
+\[ C_i = \frac{2|\{e_{jk}: v_j,v_k \in N_i, e_{jk} \in E\}|}{k_i(k_i-1)} \]
 
+From this \textit{Local Clustering Coefficient} $\overline{C_i}$, we can then take the average over the entire set of nodes in the graph.
 \[ \overline{C^\Delta} = \frac{1}{|P|}\sum^{|P|}_{i=1}C_i \]
+
+It is important to note that although the terminology is similar\cite{uzzi2005collaboration}, $\overline{C^\Delta}$ and $C^\Delta$ are different measurements.
 Unless otherwise noted, the Transitivity version of this metric ($C^\Delta$) will be used for all further calculations and metrics.

### 2013-11-21 paper/main.tex
Fixed a typo.

@@
 \noindent\\\textit{Q4: What are some characteristics of a high performing team?}\\
-\noindent\\\textit{Q5: In your experience, is it better to (A) keep an innovative team intact, (B) periodically bring in new members or re-assign exising members, or (C) split up and disperse the team to as many other projects as possible?}\\
+\noindent\\\textit{Q5: In your experience, is it better to (A) keep an innovative team intact, (B) periodically bring in new members or re-assign existing members, or (C) split up and disperse the team to as many other projects as possible?}\\
 

### 2013-11-23 paper/interview1.tex
Added start of interview.

\clearpage

\section*{Appendix A: Interview Transcript}
Interview with Traci St. Martin, PMP\textregistered, Mayo Clinic, Nov 21, 2013.

\subsection*{Q1: How do development teams collaborate and share ideas?}

\subsection*{Q2: Do teams generally remain intact over multiple projects, or do members often shuffle and re-combine?}

\subsection*{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project.}

\subsection*{Q4: What are some characteristics of a high performing team?}

\subsection*{Q5: In your experience, is it better to (A) keep an innovative team intact, (B) periodically bring in new members or re-assign existing members, or (C) split up and disperse the team to as many other projects as possible?}

### 2013-11-26 paper/interview1.tex
Updated code to display true Q value.

@@
 \subsection*{Q1: How do development teams collaborate and share ideas?}
+Co-location is important for teams, as it really fosters communication and collaboration.
+Being able to quickly talk with someone and resolve a problem is very important.
+In some cases, having the team in the same room is beneficial, especially if the project is going badly.
+That way, ideas can get discussed and problems resolved very quickly.
+Regular meetings are also important with large teams.
+With these meetings, it is important to have the correct tools to facilitate communication.
+These meetings help projects have visibility into each other.
+Management support is essential to this communication process.
+Meetings between teams can consist of all members of the teams if the teams are small enough, but most of the time should just be a representative.
 
 \subsection*{Q2: Do teams generally remain intact over multiple projects, or do members often shuffle and re-combine?}
+I have had both.
+It really depends on the projects and the situation at the time.
+It can be nice to have new people brought in to make things different, and to bring some new thoughts and ideas to the team.
+Even one person can change the dynamics of a team, either positively or negatively.
+As a project manager, I have to be watchful of this, as negativity can spread quickly.
+I have also noticed that as people move around to different projects, they are generally brought up to the level of the team.
+For example, if somebody joins a high performing team, they tend to elevate their skill to match that of the group, which is a good thing.
 
 \subsection*{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project.}
+Familiarity is good, but you have to account for burnout if people work on the same project for too long.
+This really depends on project dynamics, special skills needed, etc.
+It is important to note, however, that team members can be familiar with each other but not get along well, or not work well with each other.
+I have had projects where team members were very familiar with each other, but did not function well as a team.
+Clashing personalities and other team problems can cause a toxic environment.
+Most importantly, whether the team is familiar with each other or not, is that they can share knowledge and skills.
 
 \subsection*{Q4: What are some characteristics of a high performing team?}
+Most teams I notice go through the Forming, Storming, Norming and Performing stages.
+Good teams usually have a strong leader, a good vision, and good management support.
+Of course, they also possess the necessary skills for the project (or, if not, are willing to learn).
+Good teams have respect for each other, their leadership, and their management.
+Professionalism is also an indicator of a high performing team.
+Teams that truly care about their job, the team, and the project are generally more successful.
+Teams are generally more successful if the individuals themselves are skilled and talented.
+Being able to react to change is important, and good teams generally have good change management procedures.
 
 \subsection*{Q5: In your experience, is it better to (A) keep an innovative team intact, (B) periodically bring in new members or re-assign existing members, or (C) split up and disperse the team to as many other projects as possible?}
+In general, I like to keep good teams intact.
+It is, however, nice to bring in or add a new member to a team.
+One strategy I like to employ is to bring in a new member, train them and let them learn from the high performing team, and move them out of the project and into a new one.
+This keeps the core team intact, which is important.
+Priorities can greatly influence this, and sometimes personnel moves are driven from higher management priorities.
+If experts are removed from a high performing team, the team may suffer.
+This is, however, a risk that knowledge becomes concentrated.
+High priority/high visibility teams have a tendency to get the highest performing individuals, which can cause other projects to suffer.

### 2013-11-26 paper/interview2.tex
Updated code to display true Q value.

\clearpage

\section*{Appendix B: Interview Transcript}
Interview with M Iftekhar (Ifte) Rana, PMP\textregistered, Mayo Clinic, Nov 21, 2013.

\subsection*{Q1: How do development teams collaborate and share ideas?}

\subsection*{Q2: Do teams generally remain intact over multiple projects, or do members often shuffle and re-combine?}

\subsection*{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project.}

\subsection*{Q4: What are some characteristics of a high performing team?}

\subsection*{Q5: In your experience, is it better to (A) keep an innovative team intact, (B) periodically bring in new members or re-assign existing members, or (C) split up and disperse the team to as many other projects as possible?}

### 2013-11-26 paper/main.tex
Added start of interview.
Updated code to display true Q value.

@@
 \section{Introduction}
-A social network is a graph people and the interactions between them.
+A social network is a graph of people and the connections between them.
 The dynamics of social networks have proved to be an important research topic for many different areas of study, from academic publication\cite{barabasi2002evolution}, to the success of broadway musicals\cite{uzzi2005collaboration}.
@@
 
-A `small world' network is a social network characterized by high clustering of graph nodes paired with a short average path between nodes \cite{watts1998collective}.
-`Clustering' in this context means how closely nodes in the graph are related to each other, or "the friend of my friend is also my friend." Milgram, in is seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}.
-From these observations, hypotheses can be made as to the efficiency of how knowledge is transfered in these groups\cite{latora2001efficient}.
-In this work, we investigate the `small world' phenomenon and how it relates to Software Project Teams.
+A `small world' network is a social network characterized by high clustering of graph nodes paired with a short average path between nodes\cite{watts1998collective}.
+`Clustering' in this context means how closely nodes in the graph are related to each other, or "the friend of my friend is also my friend." Milgram, in is seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}, or in other words, the average `path length' between any two people.
+
+Uzzi \cite{uzzi2005collaboration} expanded on this by exploring how these small world networks correlate to collaboration and creativity.
+In his study, the network of artists involved in the making of Broadway musicals from 1945 to 1989 were studied.
+Performance of the musicals were then measured based on financial success and critical acclaim, and compared that quantitative analysis to the clustering and path length of the graph.
+
+We follow Uzzi's work, and expand it to software teams.
+We hypothesize that the qualities of a small world graph that foster collaboration, creativity, and the efficiency of how knowledge is transfered\cite{latora2001efficient} will also apply to software project teams.
+In this work, we investigate the `small world' phenomenon quantitatively by exploring open source project data, and qualitatively by a series of interviews of subject matter experts, and look to compare Uzzi's findings to ours.
 
@@
 Data was collected using the freely available FLOSSmole\cite{floss2006} data sets of free and open source projects.
-The data collection used was collected from the popular open source project site FreeCode\footnote{http://freecode.com/}, and contains data up to September, 2013.
+The data collection used was collected from the popular open source project site FreeCode,\footnote{http://freecode.com/} and contains data up to September, 2013.
 Results were analyzed using the Python graph processing packaged NetworkX\cite{hagberg-2008-exploring}.
@@
 The collected data was organized into a graph structure, with the nodes representing the projects and the edges representing one or more shared developer between projects.
-Various properties of the graph are analyzied, as indicated in the sections below.
+Various properties of the graph are analyzed, followed by a qualitative section to help link the quantitative analysis to subject matter expert experiences.
 
@@
 From this large disconnected graph, each connected subgraph is analyzed.
-Metrics are computed for each of these subgraphs, and a total subgraph performance is computed by averaging the performance value of each graph in the subgraph.
-We measure a subgraph's perfomance by the FreeCode \textit{Popularity Score} metric, which is calculated the following formula\footnote{http://help.freecode.com/kb/statistics/how-do-you-measure-a-projects-popularity}:
+Metrics are computed for each of these subgraphs, and a total subgraph performance value is computed by averaging the performance value of each graph in the subgraph.
+We measure a subgraph's performance by the FreeCode \textit{Popularity Score} metric, which is calculated the following formula\footnote{http://help.freecode.com/kb/statistics/how-do-you-measure-a-projects-popularity}:
 
@@
 
+The FreeCode data can be represented as a bipartite graph.
 A bipartite graph is a specialized type of graph containing two disjoint sets of verticies.
@@
 
-A bipartite graph projection.
-in necessary to further analyze the graph.
+A bipartite graph projection is necessary to further analyze the graph.
 A bipartite projection involves taking the disjoint node sets $P$ and $C$, and representing the graph as relationships between only one of those sets of nodes.
@@
 
-\noindent\\\textit{Clustering Coefficient - Transitivity ($C^\Delta$)}\\
+\noindent\\\textit{\textbf{Clustering Coefficient - Transitivity ($C^\Delta$)}}\\
 We calculate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
@@
 
-\noindent\\\textit{Clustering Coefficient - Average ($\overline{C^\Delta}$)}\\
+This metric shows us how closely related, or ``clustered,'' that the graph is.
+It is also the probability that two nodes will be connected if they share a common neighbor\cite{newman2003properties}.
+In our context, if project $P_1$ and $P_2$ share a developer with $P_3$, this metric represents the probability that $P_1$ and $P_2$ will share a developer.
+
+\noindent\\\textit{\textbf{Clustering Coefficient - Average ($\overline{C^\Delta}$)}}\\
 Another approach to clustering is to take the average of each node's local clustering coefficient\cite{watts1998collective}.
@@
 
-\noindent\\\textit{Average Path Length ($L$)}\\
+\noindent\\\textit{\textbf{Average Path Length ($L$)}}\\
 Also, calculating the \textit{Path Length} ($L$) allows us to determine how far removed developers in the graph are from one another.
@@
 
-\noindent\\\textit{Small World Quotient ($Q$)}\\
+\noindent\\\textit{\textbf{Small World Quotient ($Q$)}}\\
 The \textit{Small World Quotient} ($Q$) is defined as the Clustering Coefficient ($C^\Delta$) divided by the  Average Path Length ($L$)\cite{watts1999small,watts1998collective}.
@@
 \[Q =  \frac{C^\Delta}{L}\]
+
+Calculating $Q$ allows us to
 
@@
 
-\noindent\\\textit{Small-World-ness ($S^\Delta$)}\\
+\noindent\\\textit{\textbf{Small-World-ness ($S^\Delta$)}}\\
 The definition of a \textit{small world} graph can be formalized by the following equations\cite{humphries2008network}.
@@
 
-\noindent\\\textit{Successful vs Unsuccessful}\\
+\noindent\\\textit{\textbf{Successful vs Unsuccessful}}\\
 To further explore the data, a comparion was made between \textit{successful} and \textit{unsuccessful} projects was made.
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.5\textwidth]{images/freecode-smallworld-histo.png}
-\end{center}
-\caption{$S^\Delta$ Distribution}
-\label{fig:sw_distribution}
-\end{figure}
-
 \subsection{Qualitative}
@@
 
+\input{interview1}
+\input{interview2}
+
 \end{document}

### 2013-11-26 code/analyze_graph.py

@@ -2,12 +2,12 @@ import networkx as nx
 import csv
 import itertools
 import matplotlib.pyplot as plt
-import random
 import numpy as np
 import table
 
 def read_contributors():
     contributors = {}
+    projects = {}
 
     fp = file('../data/fcProjectAuthors2013-Sep.txt')
     csvreader = csv.DictReader(filter(lambda row: row[0]!='#', fp), delimiter='\t')
@@ -16,11 +16,14 @@ def read_contributors():
         project = row['project_id'].strip()
         if contributor not in contributors:
             contributors[contributor] = []
+        if project not in projects:
+            projects[project] = []
 
         contributors[contributor].append(project)
+        projects[project].append(contributor)
     fp.close()
 
-    return contributors
+    return contributors,projects
 
 
 def read_stats():
@@ -48,7 +51,7 @@ def read_stats():
 def reject_outliers(data):
     return data
 
-def get_small_worldness(q_dict_g, q_dict_rand):
+def get_q(q_dict_g, q_dict_rand):
     """
     Humphries, M. D., & Gurney, K. (2008).
     Network 'small-world-ness': a quantitative method for determining canonical network equivalence. PLoS One, 3(4), e0002051.
@@ -62,50 +65,35 @@ def get_small_worldness(q_dict_g, q_dict_rand):
 
         return (C_g/C_rand) / (L_g/L_rand)
     except ZeroDivisionError:
-       return None
+        return None
 
 
-def compute_q(graph):
+def compute_stats(graph):
     cc = nx.transitivity(graph)
     pl = nx.average_shortest_path_length(graph)
     avg_cc = nx.average_clustering(graph, weight="weight")
 
-    return {"q":cc/pl,"pl":pl,"cc":cc, "avg_cc": avg_cc}
+    return {"pl":pl,"cc":cc, "avg_cc": avg_cc}
 
-def compute_random_graph(nodes, edges):
+def compute_random_graph(nodes, edges, g):
 
-    graph_r = nx.Graph()
+    degrees = sum(g.degree().values())
+    avg_degree = (float(degrees)/float(nodes))
+    try:
+        return nx.connected_watts_strogatz_graph(nodes, int(avg_degree), 0.5)
+    except nx.NetworkXPointlessConcept:
+        assert (edges == (nodes - 1))
+        return g
 
-    node_range = range(0,nodes)
-
-    random_edges = 0
-
-    last_node = None
-    for i in node_range:
-        if last_node is None:
[…]

### 2013-11-26 paper/main.tex
New graphs.

@@
 
-\noindent\\\textit{\textbf{Clustering Coefficient - Transitivity ($C^\Delta$)}}\\
+\noindent\\\textit{\textbf{Clustering Coefficient - Transitivity ($C$)}}\\
 We calculate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
@@
 
-\noindent\\\textit{\textbf{Clustering Coefficient - Average ($\overline{C^\Delta}$)}}\\
+\noindent\\\textit{\textbf{Clustering Coefficient - Average ($\overline{C}$)}}\\
 Another approach to clustering is to take the average of each node's local clustering coefficient\cite{watts1998collective}.
@@
 We only consider path length for connected subgraphs, avoiding some complexities of this calculation on disconnected graphs\cite{boccaletti2006complex}.
-
-\noindent\\\textit{\textbf{Small World Quotient ($Q$)}}\\
-The \textit{Small World Quotient} ($Q$) is defined as the Clustering Coefficient ($C^\Delta$) divided by the  Average Path Length ($L$)\cite{watts1999small,watts1998collective}.
-
-\[Q =  \frac{C^\Delta}{L}\]
-
-Calculating $Q$ allows us to
 
@@
 
-\noindent\\\textit{\textbf{Small-World-ness ($S^\Delta$)}}\\
-The definition of a \textit{small world} graph can be formalized by the following equations\cite{humphries2008network}.
+\noindent\\\textit{\textbf{Small World Quotient ($Q$)}}\\
+The definition of a \textit{small world} graph can be formalized by the following equations\cite{humphries2008network,uzzi2005collaboration}.
 
@@
 
-Finally, the ratio of the above calculations yields the small-world-ness, or $S^\Delta$, of the graph
-\[S^\Delta = \frac{\gamma^{\Delta}_g }{\lambda_g} \]
+Finally, the ratio of the above calculations yields the small world quotient, or $Q$, of the graph
+\[Q = \frac{\gamma^{\Delta}_g }{\lambda_g} \]
 
-We assume for throughout that any graph exhibiting $S^\Delta > 1$ is a small-world graph.
+We assume for throughout that any graph exhibiting $Qa > 1$ is a small-world graph.
 
@@
 Summary statistics for the graph analysis are captured in figure \ref{fig:summary_stats}.
-First, $S^\Delta > 1$ is observed for both the mean and the median, which meets the criteria for a small-world network\cite{humphries2008network}.\\
+Importantly, $Q > 1$ is observed for both the mean and the median, which meets the criteria for a small-world network\cite{humphries2008network}.\\
 
-$Q$ and $C^\Delta$ both indicate a non-normal distribution, as shown by the large standard deviation.
-This observation indicates a propensity towards the extremes of these measurements.
-This is further reinforced by the distribution of $Q$ shown in figure \ref{fig:q_distribution}.
-This figure indicates that the majority of subgraphs have a $Q$ and $C^\Delta$ value of close to either 0 or 1.\\
+$C$ and $\overline{C}$ both indicate values approaching 1.
+This observation indicates a high degree of clustering\cite{watts1998collective}.
+hat any indicates that the majority of subgraphs have a $Q$ and $C^\Delta$ value of close to either 0 or 1.
+Exploring this phenomenon further, we can derive that most graphs resemble the middle or the bottom graph in figure \ref{fig:example_graphs}, with relatively few resembling the top graph.
 
-Exploring this phenomenon further, follows that most graphs resemble the top or the middle graph in figure \ref{fig:example_graphs}, with relatively few resembling the bottom graph.
-
-To validate the hypothesis, we expect to find that medium values of $C^\Delta$ will be correlated with more popular projects.
-To explore this possibility, we first compare the popularity given $C^\Delta$ values as shown in figure \ref{fig:cc_graph}.
-The $C^\Delta$ values do display the U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi \textit{et.
+To validate the hypothesis, we expect to find that medium values of $Q$ will be correlated with more popular projects.
+To explore this possibility, we first compare the popularity given $Q$ values as shown in figure \ref{fig:cc_graph}.
+The $Q$ values do display the U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi \textit{et.
 al}\cite{uzzi2005collaboration}.
-It is important to note, however that, the standard deviation is high, as shown in both \ref{fig:summary_stats} and the significant difference between the mean and median results.
 
@@
 Popular projects do appear to conform to the results found by Uzzi\cite{uzzi2005collaboration}.
-As show in figure \ref{fig:cc_unpopular}, $C^\Delta$ near the extremes (0.0 or 1.0) show a relatively low likelihood of being popular.
-As $C^\Delta$ values approach mid-range values, the probability of a project being a success increases greatly.
+As show in figure \ref{fig:cc_popular}, $Q$ near the extremes show a relatively low likelihood of being popular.
+As $Q$ values approach mid-range values, the probability of a project being a success increases greatly.
 
@@
 \end{center}
-\caption{$C^\Delta$ of Popular Projects}
+\caption{$Q$ of Popular Projects}
 \label{fig:cc_popular}
@@
 The inverse is true of unpopular projects.
-As $C^\Delta$ near the extremes (0.0 or 1.0), a high probability of being unsuccessful is observed.
-Mid-valued $C^\Delta$ values indicate a substantially lower probability of being unsuccessful.
+As $Q$ near the extremes, a high probability of being unsuccessful is observed.
+Mid-valued $Q$ values indicate a substantially lower probability of being unsuccessful.
 
@@
 \end{center}
-\caption{$C^\Delta$ of Unpopular Projects}
+\caption{$Q$ of Unpopular Projects}
 \label{fig:cc_unpopular}
@@
 
-Distribution of $Q$ values are shown in figure\ref{fig:q_distribution}. This indicates that the majority of sub-graphs have a $Q$ value near either 0.0 or 1.0.
+Distribution of $Q$ values are shown in figure\ref{fig:q_distribution}.
+The values of $Q$ generally follow a power-law distribution, with most values being at our around $Q = 1$.
+This indicates that many graphs are close to the delineation of being considered small-world\cite{humphries2008network}.
 

### 2013-11-26 code/analyze_graph.py

@@ -151,17 +151,17 @@ def graph(name, data, popularity):
 
         popularity_score.append(avg_popularity)
 
-    bins = np.linspace(min(q),max(q), num=8)
-    values = [[] for _ in bins]
+    q_bins = np.linspace(min(q),max(q), num=8)
+    q_values = [[] for _ in q_bins]
 
-    idxs = np.digitize(q, bins, right=True)
+    q_idxs = np.digitize(q, q_bins, right=True)
 
-    for idx,score in zip(idxs,popularity_score):
-        values[idx].append(score)
+    for idx,score in zip(q_idxs,popularity_score):
+        q_values[idx].append(score)
 
-    create_graph(name, bins, values)
+    create_graph(name, q_bins, q_values)
     create_histogram(name + "-q", "$Q$", q, log_y_scale=True)
-    highest_performing(name, bins, values)
+    highest_performing(name, q_bins, q_values)
 
     total_projects = len(set(sum(contributors.values(), [])))
 
@@ -197,7 +197,7 @@ def highest_performing(filename, bins, values):
     unpopular_bins = []
 
     for bin,value in zip(bins,values):
-        if len(value) < 5: continue
+        if len(value) < 3: continue
         popular_repos = len([v for v in value if v > 100])
         unpopular_repos = len([v for v in value if v < 100 ])
         print str(bin) + " " + str(popular_repos) + " " + str(unpopular_repos) + " " + str(len(value))
@@ -208,7 +208,7 @@ def highest_performing(filename, bins, values):
 
     for name, data in zip(["popular","unpopular"], [popular_bins,unpopular_bins]):
         fig = plt.figure()
-        plt.hist(data, len(bins), color="0.75")
+        plt.hist(data, 4, color="0.75")
         plt.xlabel("$Q$")
         plt.ylabel("% " + name)
         F = plt.gcf()

### 2013-11-26 paper/main.tex
Last draw of diagrams.

@@
 
-Popular projects do appear to conform to the results found by Uzzi\cite{uzzi2005collaboration}.
-As show in figure \ref{fig:cc_popular}, $Q$ near the extremes show a relatively low likelihood of being popular.
-As $Q$ values approach mid-range values, the probability of a project being a success increases greatly.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.5\textwidth]{images/freecode-popular.png}
-\end{center}
-\caption{$Q$ of Popular Projects}
-\label{fig:cc_popular}
-\end{figure}
-
-The inverse is true of unpopular projects.
-As $Q$ near the extremes, a high probability of being unsuccessful is observed.
-Mid-valued $Q$ values indicate a substantially lower probability of being unsuccessful.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.5\textwidth]{images/freecode-unpopular.png}
-\end{center}
-\caption{$Q$ of Unpopular Projects}
-\label{fig:cc_unpopular}
-\end{figure}
-
 Distribution of $Q$ values are shown in figure\ref{fig:q_distribution}.

### 2013-11-26 code/analyze_graph.py

@@ -4,6 +4,7 @@ import itertools
 import matplotlib.pyplot as plt
 import numpy as np
 import table
+from collections import OrderedDict
 
 def read_contributors():
     contributors = {}
@@ -161,21 +162,20 @@ def graph(name, data, popularity):
 
     create_graph(name, q_bins, q_values)
     create_histogram(name + "-q", "$Q$", q, log_y_scale=True)
-    highest_performing(name, q_bins, q_values)
 
     total_projects = len(set(sum(contributors.values(), [])))
 
     write_table("subgraphs_summary",
                 table.create_table("Summary", "fig:summary_stats", "Projects: %s, Subgraphs: %s, Contributors: %s" % (total_projects, N, len(contributors.keys())),
-                                   {
-                                       "$Q$": q,
-                                       "$C$": cc,
-                                       "$\overline{C}$": avg_cc,
-                                       "$L$": pl,
-                                       "Popularity": popularity_score,
-                                       "Nodes": subgraph_node_number,
-                                       "Edges": subgraph_edge_number
-                                   }))
+                                   OrderedDict([
+                                       ("$Q$", q),
+                                       ("$C$", cc),
+                                       ("$\overline{C}$", avg_cc),
+                                       ("$L$", pl),
+                                       ("Popularity",popularity_score),
+                                       ("Nodes", subgraph_node_number),
+                                       ("Edges", subgraph_edge_number)
+                                   ])))
 
 def write_table(file_name, table_tex):
     with open("../paper/tables/"+file_name+".tex", 'w') as the_file:
@@ -191,29 +191,6 @@ def create_histogram(filename, x_label, data, log_y_scale=False):
     F = plt.gcf()
     F.savefig("../paper/images/"+filename+"-histo.png")
     plt.close(fig)
-
-def highest_performing(filename, bins, values):
-    popular_bins = []
-    unpopular_bins = []
-
-    for bin,value in zip(bins,values):
-        if len(value) < 3: continue
-        popular_repos = len([v for v in value if v > 100])
-        unpopular_repos = len([v for v in value if v < 100 ])
-        print str(bin) + " " + str(popular_repos) + " " + str(unpopular_repos) + " " + str(len(value))
-        for _ in range(int( (float(popular_repos) / len(value)) * 100 )):
-            popular_bins.append(bin)
[…]

### 2013-11-26 paper/main.tex
Added interview citations.

@@
 \textit{Software Project Teams will perform best at moderate levels of $Q$.
-This performance, measured by the number of interest their projects generate, will increase as the level of $Q$ increases for the developer graph.
+This performance, measured by the amount of interest their projects generate, will increase as the level of $Q$ increases for the developer graph.
 This will continue up to an optimal $Q$ value, after which performance will begin to degrade.
-Thus, the performance curve given $Q$ will be U-shaped, and match Uzzi's findings\cite{uzzi2005collaboration}.}
+Thus, the performance curve given $Q$ will be inverse U-shaped, and match Uzzi's findings\cite{uzzi2005collaboration}.}
 
@@
 A bipartite projection involves taking the disjoint node sets $P$ and $C$, and representing the graph as relationships between only one of those sets of nodes.
-A projection onto the project nodes, or $P$, of figure \ref{fig:example_bipartite_graph} is show in figure \ref{fig:example_bipartite_projection_graph}.
-Here, projects are connected directly, with edges occurring if one or more developer is shared between the projects.
-It is important to note that the projection could have been done in terms of the contributors, not the projects.
-This would have led to a graph with nodes of contributors $C$, each being linked by sharing a common project.
-This approach is another common way of representing these bipartite graphs\cite{newman2001scientific}, and illustrates the fact that a bipartite projections are lossy compared to the data reprented in the original graph\cite{zhou2007bipartite}.\\
+A projection onto the contributor nodes, or $C$, of figure \ref{fig:example_bipartite_graph} is show in figure \ref{fig:example_bipartite_projection_graph}.
+Here, contributors are connected directly, with edges occurring if a two contributors share one or more common projects.
+It is important to note that the projection could have been done in terms of the projects, not the contributors.
+This would have led to a graph with nodes of projects $P$, each being linked by sharing a common contributor.
+This approach is a common way of representing these bipartite graphs\cite{newman2001scientific}, and illustrates the fact that a bipartite projections are lossy compared to the data represented in the original graph\cite{zhou2007bipartite}.\\
 
-One of the main sources of information loss is multiple connections between projects, or projects that share multiple collaborators.
-When doing a bipartite projection based on projects $P$, a single link could represent one shared developer or many.
+One of the main sources of information loss is multiple connections between contributors, or contributors that share multiple projects.
+When doing a bipartite projection based on contributors $C$, a single link could represent one shared project or many.
 This is a source of data loss in the projection.
@@
 \begin{tikzpicture}
-\tikzset{P/.style={circle,fill=lightgray!20}}
 \tikzset{C/.style={circle,fill=black!20}}
@@
  [scale=.5,auto=left]
-  \node[P] (p1) at (-5,3)  {$P_1$};
-  \node[P] (p2) at (-3,2)  {$P_2$};
-  \node[P] (p3) at (-5,1)  {$P_3$};
-  \node[P] (p4) at (-2,1)  {$P_4$};
+  \node[C] (c1) at (-5,3)  {$C_1$};
+  \node[C] (c2) at (-3,2)  {$C_2$};
+  \node[C] (c3) at (-5,1)  {$C_3$};
+  \node[C] (c4) at (-2,1)  {$C_4$};
 
-  \draw ({p1}) -- ({p3});
-  \draw ({p1}) -- ({p2});
-  \draw ({p1}) -- ({p2});
-  \draw ({p2}) -- ({p3});
-  \draw ({p3}) -- ({p4});
+  \draw ({c1}) -- ({c3});
+  \draw ({c1}) -- ({c2});
+  \draw ({c1}) -- ({c2});
+  \draw ({c2}) -- ({c3});
+  \draw ({c3}) -- ({c4});
 \end{tikzpicture}
-\caption{A $P$ projection of the figure \ref{fig:example_bipartite_graph} bipartite graph}
+\caption{A contributor ($C$) projection of the figure~\ref{fig:example_bipartite_graph} bipartite graph}
 \label{fig:example_bipartite_projection_graph}
@@
 It is also the probability that two nodes will be connected if they share a common neighbor\cite{newman2003properties}.
-In our context, if project $P_1$ and $P_2$ share a developer with $P_3$, this metric represents the probability that $P_1$ and $P_2$ will share a developer.
+In our context, if contributors $C_1$ and $C_2$ both collaborate with a common contributor w $C_3$, this metric represents the probability that $C_1$ and $C_2$ will collaborate.
 
@@
 \end{center}
-\caption{$C^\Delta$ and Project Popularity}
+\caption{$Q$ and Project Popularity}
 \label{fig:cc_graph}
@@
 
-Small-world-ness, or $S^\Delta$, is generally between 1 and 3 for most sub-graphs.
+Small-world-ness, or $Q$, is generally between 1 and 3 for most sub-graphs.
 

### 2013-11-26 code/analyze_graph.py
Added SourceForge data.

@@ -6,7 +6,7 @@ import numpy as np
 import table
 from collections import OrderedDict
 
-def read_contributors():
+def read_contributors_fc():
     contributors = {}
     projects = {}
 
@@ -27,7 +27,7 @@ def read_contributors():
     return contributors,projects
 
 
-def read_stats():
+def read_stats_fc():
     popularity = {}
 
     fp = file('../data/fcProjectStats2013-Sep.txt')
@@ -48,6 +48,48 @@ def read_stats():
 
     return popularity
 
+
+def read_contributors_sf():
+    contributors = {}
+    projects = {}
+
+    fp = file('../data/sfRawDeveloperProjectData2009-Jun.txt')
+    csvreader = csv.DictReader(filter(lambda row: row[0]!='#', fp), delimiter='\t')
+    for row in csvreader:
+        contributor = row['dev_loginname'].strip()
+        project = row['proj_unixname'].strip()
+        if contributor not in contributors:
+            contributors[contributor] = []
+        if project not in projects:
+            projects[project] = []
+
+        contributors[contributor].append(project)
+        projects[project].append(contributor)
+    fp.close()
+
+    return contributors,projects
+
+
+def read_stats_sf():
+    popularity = {}
+
+    fp = file('../data/sfRawRanksData2009-Jun.txt')
+    csvreader = csv.DictReader(filter(lambda row: row[0]!='#', fp), delimiter='\t')
+    for row in csvreader:
+        project_id = row['proj_unixname'].strip()
+        popularity_score = row['round(avg(rank))'].strip()
+
+        try:
+            score = float(popularity_score)
+        except ValueError, e:
+            print "ERROR calculating project score: %s" % str(popularity_score)
+            score = 0
+
+        if project_id not in popularity: popularity[project_id] = score
+
+    fp.close()
+
+    return popularity
 
 def reject_outliers(data):
     return data
@@ -119,6 +161,8 @@ def graph(name, data, popularity):
         nodes = subgraph.number_of_nodes()
         edges = subgraph.number_of_edges()
 
+        if nodes > 10000: continue
+
         if nodes < 3: continue
 
         subgraph_node_number.append(nodes)
@@ -165,16 +209,15 @@ def graph(name, data, popularity):
 
     total_projects = len(set(sum(contributors.values(), [])))
 
-    write_table("subgraphs_summary",
[…]

### 2013-11-26 code/table.py

@@ -15,8 +15,8 @@ def create_table(title,label,caption,stats,functions=summary_functions):
     table = ""
     table += "\\begin{table}[htbp]\centering\n"
     table += "\caption{\label{"+label+"}\n"
-    table += "\\textbf{Statistics} }\\begin{tabular} {@{} l r "+ "".join(" r " for _ in range(len(functions))) +" @{}} \\\ \hline\n"
-    table += "\\textbf{Statistic} & " + " & ".join(["\\textbf{%s}" % key for key in functions.keys()]) + " \\\ \n"
+    table += "\\textbf{"+title+"} }\\begin{tabular} {@{} l r "+ "".join(" r " for _ in range(len(functions))) +" @{}} \\\ \hline\n"
+    table += "\\textbf{Var} & " + " & ".join(["\\textbf{%s}" % key for key in functions.keys()]) + " \\\ \n"
     table += "\hline\n"
     table += "".join([s + " & " + " & ".join([str(f(stats[s])) for k,f in functions.items()]) + " \\\ \n" for s in stats])
     table += "\hline\n"

### 2013-11-26 paper/main.tex
Added SourceForge data.
Updated var names.

@@
 
-\noindent\\\textit{\textbf{Clustering Coefficient - Transitivity ($C$)}}\\
+\noindent\\\textit{\textbf{Clustering Coefficient - Transitivity ($C^\Delta$)}}\\
 We calculate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
@@
 
-\noindent\\\textit{\textbf{Clustering Coefficient - Average ($\overline{C}$)}}\\
+\noindent\\\textit{\textbf{Clustering Coefficient - Average ($\overline{C^{\lambda}}$)}}\\
 Another approach to clustering is to take the average of each node's local clustering coefficient\cite{watts1998collective}.
@@
 To do this, we take the number of actual connections between neighbors divided by the total possible number of connections, where $k_i$ represents the count of the neighbors of a node, or {$k_i = |N_i|$}
-\[ C_i = \frac{2|\{e_{jk}: v_j,v_k \in N_i, e_{jk} \in E\}|}{k_i(k_i-1)} \]
+\[ C^{\lambda}_i = \frac{2|\{e_{jk}: v_j,v_k \in N_i, e_{jk} \in E\}|}{k_i(k_i-1)} \]
 
-From this \textit{Local Clustering Coefficient} $\overline{C_i}$, we can then take the average over the entire set of nodes in the graph.
-\[ \overline{C^\Delta} = \frac{1}{|P|}\sum^{|P|}_{i=1}C_i \]
+From this \textit{Local Clustering Coefficient} $C_i$, we can then take the average over the entire set of nodes in the graph.
+\[ \overline{C^\lambda} = \frac{1}{|P|}\sum^{|P|}_{i=1}C^{\lambda}_i \]
 
-It is important to note that although the terminology is similar\cite{uzzi2005collaboration}, $\overline{C^\Delta}$ and $C^\Delta$ are different measurements.
+It is important to note that although the terminology is similar\cite{uzzi2005collaboration}, $\overline{C^\lambda}$ and $C^\Delta$ are different measurements.
 Unless otherwise noted, the Transitivity version of this metric ($C^\Delta$) will be used for all further calculations and metrics.
@@
 
-We assume for throughout that any graph exhibiting $Qa > 1$ is a small-world graph.
+We assume for throughout that any graph exhibiting {$Q > 1$} is a small-world graph.
 
@@
 
-\input{tables/subgraphs_summary}
+\input{tables/subgraphs_summary_freecode}
+\input{tables/subgraphs_summary_sf}
 
@@
 
-$C$ and $\overline{C}$ both indicate values approaching 1.
+$C^\Delta$ and $\overline{C^\lambda}$ both indicate values approaching 1.
 This observation indicates a high degree of clustering\cite{watts1998collective}.
@@
 \caption{$Q$ and Project Popularity}
-\label{fig:cc_graph}
+\label{fig:q_fc_graph}
 \end{figure}
 
-Distribution of $Q$ values are shown in figure\ref{fig:q_distribution}.
-The values of $Q$ generally follow a power-law distribution, with most values being at our around $Q = 1$.
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.5\textwidth]{images/sf-graph.png}
+\end{center}
+\caption{$Q$ and Project Popularity}
+\label{fig:q_sf_graph}
+\end{figure}
+
+Distribution of $Q$ values are shown in figures\ref{fig:fc_q_distribution,fig:sf_q_distribution}.
+The values of $Q$ generally follow a power-law distribution, with most values being at our around {$Q = 1$}.
 This indicates that many graphs are close to the delineation of being considered small-world\cite{humphries2008network}.
@@
 \caption{$Q$ Distribution}
-\label{fig:q_distribution}
+\label{fig:q_fc_distribution}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.5\textwidth]{images/sf-q-histo.png}
+\end{center}
+\caption{$Q$ Distribution}
+\label{fig:q_sf_distribution}
 \end{figure}

### 2013-11-26 code/analyze_graph.py

@@ -213,8 +213,8 @@ def graph(name, data, popularity):
                 table.create_table("Summary", "fig:summary_stats", "P: %s, $P_c$: %s, C: %s" % (total_projects, N, len(contributors.keys())),
                                    OrderedDict([
                                        ("$Q$", q),
-                                       ("$C$", cc),
-                                       ("$\overline{C}$", avg_cc),
+                                       ("$C^{\Delta}$", cc),
+                                       ("$\overline{C^{\lambda}}$", avg_cc),
                                        ("$L$", pl),
                                        ("N", subgraph_node_number),
                                        ("E", subgraph_edge_number)

### 2013-11-27 paper/main.tex
Working on conclusions.

@@
 Data was collected using the freely available FLOSSmole\cite{floss2006} data sets of free and open source projects.
-The data collection used was collected from the popular open source project site FreeCode,\footnote{http://freecode.com/} and contains data up to September, 2013.
+Two datasets were analyzed -- data from from the popular open source project site \textit{Freecode},\footnote{http://freecode.com/}, and another from open source software repository \textit{SourceForge}.
+The Freecode dataset contained data up to September, 2013, while the SourceForge dataset was slightly older with data gathered on June 2009.
+Both datasets were chosen because they met two basic criteria: (1) they contained an exhaustive list of projects and contributors to those projects, and (2) they provided some sort of quantitative measure of project ``popularity." This popularity metric will be further described in sectiions below.
 Results were analyzed using the Python graph processing packaged NetworkX\cite{hagberg-2008-exploring}.
@@
 \subsection{Analysis}
-The collected data was organized into a graph structure, with the nodes representing the projects and the edges representing one or more shared developer between projects.
+The collected data was organized into a graph structure, with the nodes representing the collaborators and the edges representing one or more shared project between collaborators.
 Various properties of the graph are analyzed, followed by a qualitative section to help link the quantitative analysis to subject matter expert experiences.
@@
 \subsubsection{Graph Structure}
-We first consider the FreeCode FLOSSmole\cite{floss2006} data sets to be one large graph.
-From this large disconnected graph, each connected subgraph is analyzed.
-Metrics are computed for each of these subgraphs, and a total subgraph performance value is computed by averaging the performance value of each graph in the subgraph.
-We measure a subgraph's performance by the FreeCode \textit{Popularity Score} metric, which is calculated the following formula\footnote{http://help.freecode.com/kb/statistics/how-do-you-measure-a-projects-popularity}:
-
-\[ ((record\ hits + URL\ hits) \cdot (followers + 1))^{1/2} \]
+For each dataset, we first considered the dataset to be one large graph.
+From this large disconnected graph, each connected subgraph was analyzed.
+Metrics were then computed for each of these subgraphs.
 
@@
 \begin{tikzpicture}
-\tikzset{P/.style={circle,fill=lightgray!20}}
-\tikzset{C/.style={circle,fill=black!20}}
+\tikzset{P/.style={circle,draw=black,fill=lightgray!20}}
+\tikzset{C/.style={circle,draw=black,fill=black!20}}
 
@@
 
-The FreeCode data can be represented as a bipartite graph.
+The Freecode data can be represented as a bipartite graph.
 A bipartite graph is a specialized type of graph containing two disjoint sets of verticies.
@@
 \begin{tikzpicture}
-\tikzset{C/.style={circle,fill=black!20}}
+\tikzset{C/.style={circle,draw=black,fill=black!20}}
 
@@
 \begin{tikzpicture}
-  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
+  [scale=.5,auto=left,every node/.style={circle,draw=black,fill=gray!20}]
   \node (n1) at (15,8) {1};
@@
 \begin{tikzpicture}
-  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
+  [scale=.5,auto=left,every node/.style={circle,draw=black,fill=gray!20}]
 
@@
 \begin{tikzpicture}
-  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
+  [scale=.5,auto=left,every node/.style={circle,draw=black,fill=gray!20}]
   \node (n1) at (15,7) {1};
@@
 
-\noindent\\\textit{\textbf{Successful vs Unsuccessful}}\\
-To further explore the data, a comparion was made between \textit{successful} and \textit{unsuccessful} projects was made.
-We define \textit{successful} as any project with {$PopularityScore > 100$}, and \textit{unsuccessful} as any project with {$PopularityScore < 50$}.
-Given this view of the data, we can then make assertions about how we expect these types of projects to behave, given the stated hypothesis.
-More specifically, we can examine not only if the u-shaped curve holds for \textit{popular} projects, but if the inverse holds for \textit{unsuccessful} ones.
+\noindent\\\textit{\textbf{Performance}}\\
+To further explore the data, a measurement of project performance was needed.
+As the explored datasets consisted entirely of open source projects, research indicates that \textit{quality}, \textit{use}, \textit{user satisfaction}, and \textit{impact} are possible metrics to measure performance or \textit{success}\cite{crowston2003defining}.\\
+
+For both datasets, we base our performance metric on \textit{use}.
+For Freecode, we use the \textit{Popularity Score} metric, which is calculated the following formula\footnote{http://help.freecode.com/kb/statistics/how-do-you-measure-a-projects-popularity}:
+
+\[ ((record\ hits + URL\ hits) \cdot (followers + 1))^{1/2} \]
+
+For the SourceForge dataset, performance is based on the repository's internal \textit{rank} metric.
+Note that there was no attempt to normalize the two performance metrics between datasets.
+Because of this, no cross-dataset measurements can be made, as the performance metric is only valid in the context of the enclosing dataset.
 
@@
 
+The research interviews provided a look into how some of these quantitative findings translate into actual industry practice.
+There were are few re-occurring themes that we will base our analysis on\cite{stmartin_interview,stmartin_interview}:
+
+\noindent\\\textit{\textbf{New contributors are good, as long as the core team remains intact.}}\\
+
+\noindent\\\textit{\textbf{Teams can stagnate without new members.}}\\
+
+\noindent\\\textit{\textbf{Collaboration is key to performance.}}\\
+
+\noindent\\\textit{\textbf{Priority and timeline are strong drivers.}}\\
+
 \section{Conclusion}
@@
 
-A futher area of study would be how this relates to previously defined \textit{success factors} in projects\cite{cooke2002real}.
+A further area of study would be how this relates to previously defined \textit{success factors} in projects\cite{cooke2002real}.
 

### 2013-11-29 paper/interview2.tex
Added more analysis and the last interview.

@@
 \section*{Appendix B: Interview Transcript}
-Interview with M Iftekhar (Ifte) Rana, PMP\textregistered, Mayo Clinic, Nov 21, 2013.
+Interview with M Iftekhar (Ifte) Rana, PMP\textregistered, Mayo Clinic, Nov 26, 2013.
 
 \subsection*{Q1: How do development teams collaborate and share ideas?}
+In my previous experiences, there were tight dependencies between teams and changes could have large impacts.
+Because of this, team collaboration was important and was stressed.
+Because of the tight dependencies, teams were involved in each other's planning phases.
+We found that bringing teams together during planning helped collaboration and communication.
+Also, we noticed that the quality of communication and collaboration between teams had a direct impact how how teams performed, and how the project faired as a whole.
 
 \subsection*{Q2: Do teams generally remain intact over multiple projects, or do members often shuffle and re-combine?}
+It is more of a problem when focus changes rapidly.
+If there is a stable focus for the project, and the goals of the project remain relatively intact, shifting of personnel has less impact.
+Continuously changing focus definitely has a negative impact on team performance.
+Also, when focus is changing rapidly, it is hard to maintain a stable team core, as they tend to get reassigned or loaned out to different projects.
 
 \subsection*{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project.}
+This really depends on the time-line of the project.
+Short-term projects don't have as much time for team bonding -- it is more important to get the people with the right skill set.
+For longer term projects, you have to be much more careful about people getting along with each other.
+for these types of projects, you can afford to invest some time into getting the team right and doing some team building.
+Also, with long term projects, you have more of a chance of members ``learning on the job," so even if the technical skills aren't there right away, you can factor in some learning time if they are a good fit personality-wise.
+It is the same reason why we ask a lot of behavioral questions for new full-time employees, and less so with contractors.
+It all depends on the time commitment and how much team building you can plan for.
 
 \subsection*{Q4: What are some characteristics of a high performing team?}
+The number one most important factor for a high performing team is good communication skills.
+Good teams that I've worked are highly connected, and all members of the team communication with each other.
+This leads to feedback coming from many different angles, which helps teams get better.
+Team performance is usually tied directly to how well a team communicates and shares knowledge with each other.
 
 \subsection*{Q5: In your experience, is it better to (A) keep an innovative team intact, (B) periodically bring in new members or re-assign existing members, or (C) split up and disperse the team to as many other projects as possible?}
+It is usually good to keep teams intact if they are performing well.
+That said, if you do not keep growing the team, they will quickly lose touch with changes in technology.
+New members help to bring this into the team, and if a team is isolated they often don't keep up.
+Technology trends move very quickly, so it is essential to have fast communication channels so that information can spread quickly.
+Even if new/different members aren't coming into the team, there still should be communication channels open.
+Communication between teams should happen whether or not teams are actually working together.
+In general, it is best to periodically bring in new members, but keep the core team intact if possible.

### 2013-11-29 paper/main.tex
Added more analysis and the last interview.

@@
 \subsubsection{Qualitative Analysis}
+So far we have explored, via data analysis, how closely project collaborators are connected to one another, and what correlations we can derive from this analysis.
+We have said little as to why these connections are made, how they are maintained, and what exactly a connection means at a personal level.
+Via qualitative analysis, we will attempt to enrich our data analysis by providing deeper context.\\
+A connection between two people is much more than an edge between two nodes in a graph.
 It has been asserted that people tend to make connections with people with whom they share similarities\cite{mcpherson2001birds}.
@@
 Both have had experience with project management and are certified Project Management Professionals (PMP)\textregistered.
-We proposed to them the following questions:
+We proposed to them the following questions, in hopes of expanding further the questions posed above:
 
@@
 To validate the hypothesis, we expect to find that medium values of $Q$ will be correlated with more popular projects.
-To explore this possibility, we first compare the popularity given $Q$ values as shown in figure \ref{fig:cc_graph}.
+To explore this possibility, we first compare the popularity given $Q$ values as shown in figures \ref{fig:q_fc_graph} and \ref{fig:q_sf_graph}.
 The $Q$ values do display the U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi \textit{et.
@@
 
-Distribution of $Q$ values are shown in figures\ref{fig:fc_q_distribution,fig:sf_q_distribution}.
+Distribution of $Q$ values are shown in figures \ref{fig:q_fc_distribution} and \ref{fig:q_sf_distribution}.
 The values of $Q$ generally follow a power-law distribution, with most values being at our around {$Q = 1$}.
@@
 \subsection{Qualitative}
-
 The research interviews provided a look into how some of these quantitative findings translate into actual industry practice.
+It also helped us to get a deeper understand of what what we have found in the data analysis, as we could begin to build some workplace context into our results.
 There were are few re-occurring themes that we will base our analysis on\cite{stmartin_interview,stmartin_interview}:
@@
 \noindent\\\textit{\textbf{New contributors are good, as long as the core team remains intact.}}\\
+Both participants mentioned the idea of keeping a ``core" team intact.
+This was certainly an often cited notion in both interviews.
+This concept appears to align with the idea of a \textit{core/periphery}\cite{borgatti2000models}, where the graph under study contains one (or many) tightly interconnected subgraphs, with less tightly connected nodes radiating out from this core.
+
+Although our data analysis does not include any examination of a core/periphery, it is an interesting direction for future research.
+Notably, has been suggested that individual performance in a group is highest if that individual is not in the core or the periphery, but somewhere in between\cite{cattani2008core}.
+This is especially interesting as this aligns with our hypothesis that intermediate values of $Q$ are optimal.
 
 \noindent\\\textit{\textbf{Teams can stagnate without new members.}}\\
+Both interview participants indicated that new members were essential in bringing new ideas to the team.
+A highly static team (or, a team with a high $Q$ value), runs the risk of falling behind the technology trends.
 
 \noindent\\\textit{\textbf{Collaboration is key to performance.}}\\
+Both interviewees suggested that team collaboration had a direct impact on performance.
+Teams that showed good collaboration both intra-team and inter-team were noted for their positive performance characteristics.
+Further exploration of this topic is needed to determine more fully the nature of this collaboration.
+Specifically, we know that high conflict is detrimental to team performance, especially in complex work environments\cite{de2003task}.
+A further research direction may be whether or not good team collaboration/communication promotes conflict avoidance, conflict resolution, or otherwise.
 
-\noindent\\\textit{\textbf{Priority and timeline are strong drivers.}}\\
+\noindent\\\textit{\textbf{Priority, focus, and timeline are strong drivers.}}\\
+Focus was specifically called out as an indicator of performance in one interview.
+Clear goals and a common objective were positive influencer, while continuously shifting focus was a negative influence.
+Research in this area suggests that creative teams have ``goals that are clear and compelling, but also open and challenging''\cite{isaksen2002climate}.
+
+Timeline and priority discussed as strong contributors to team success.
+Team building could be thought of as function of the timeline, meaning that as the timeline of the project increased, more time could be devoted to team building activities.
+
+It was also indicated that priority was a major factor.
+Different project priorities, and the resultant shifting of resources, had the possible effect of the weakening of string team's core members.
+This can be related to focus as well, as changing priorities can cause resource realignment and decreased overall focus.
 
@@
 \section{Acknowledgments}
+We thank Praveen Mittal and John Kaman for their insight, guidance, and instruction, M Iftekhar (Ifte) Rana and Traci St. Martin for their time and expertise, and Rick Kiefer for his review.
 

### 2013-11-30 paper/main.tex
Added correct captions to some figures.
Main content in... the revisions begin.

@@
 If follows that visualizing software team members as a graph can give some insight as to what the optimal team conditions are.
-As team members move between projects, these graphs gets more and more connected as team members make connections.
-We show that this connectivity, known as the "small world effect," has a positive impact on team performance at when the connectivity levels are moderate.
+As team members move between projects, these graphs become more and more connected as team members collaborate and form relationships.
+We show that this connectivity, known as the ``small world effect," has a positive impact on team performance when the connectivity levels are moderate.
+Performance degrades, however, at both very high and very low levels of connectivity.
 This aligns with similar research findings of non-software teams.
-We do, however, find high performance at the extremes of the connectivity range.
 \end{abstract}
@@
 \textit{Software Project Teams will perform best at moderate levels of $Q$.
-This performance, measured by the amount of interest their projects generate, will increase as the level of $Q$ increases for the developer graph.
+This performance, measured by the amount of interest their projects generate, will increase as the level of $Q$ increases for the contributor graph.
 This will continue up to an optimal $Q$ value, after which performance will begin to degrade.
@@
 Metrics were then computed for each of these subgraphs.
+In order to correctly compute the metrics below, a minimum subgraph size was required.
+Specifically, many of the graph metrics of interest measured ``triangles'' of nodes and their connections.
+This implies a subgraph of {$>= 3$} nodes is needed.
+Subgraphs of {$< 3$} nodes were not considered for analysis.
 
@@
 
-Summary statistics for the graph analysis are captured in figure \ref{fig:summary_stats}.
-Importantly, $Q > 1$ is observed for both the mean and the median, which meets the criteria for a small-world network\cite{humphries2008network}.\\
+Summary statistics for the graph analysis are captured in figure \ref{fig:summary_stats}.  Statistics analyzed included:\\
+$Q$ - \textit{Small World Quotient}\\
+$C^\Delta$ - \textit{Clustering Coefficient - Transitivity}\\
+$\overline{C^\lambda}$ - \textit{Clustering Coefficient - Average}\\
+$L$ - \textit{Average Path Length}\\
+$N$ - \textit{Number of Nodes}\\
+$E$ - \textit{Number of Edges}\\
+As measured over the number of projects $P$, with the total number of contributors $C$. The number of connected subgraphs analyzed is shown as $P_c$.
+
+A mean value of $Q$ was observed to be $> 1$ for both data sets, which meets the criteria for a small-world network\cite{humphries2008network}.
+The median, however, is 1.0 in both cases, which does not match the small world network criteria.
+A possible explanation of this is the power law distribution of $Q$ observed in both data sets (figures \ref{fig:q_fc_distribution} and \ref{fig:q_sf_distribution}.
+This indicates that a large proportion of $Q$ values are around 1.\\
 
@@
 hat any indicates that the majority of subgraphs have a $Q$ and $C^\Delta$ value of close to either 0 or 1.
-Exploring this phenomenon further, we can derive that most graphs resemble the middle or the bottom graph in figure \ref{fig:example_graphs}, with relatively few resembling the top graph.
+Exploring this phenomenon further, we can derive that most graphs resemble the middle or the bottom graph in figure \ref{fig:example_graphs}, with relatively few resembling the top graph.\\
 
-To validate the hypothesis, we expect to find that medium values of $Q$ will be correlated with more popular projects.
+Note that $P_c$ values are relatively small compared to $P$ and $C$ values.
+It would be intuitive to assume that {$C \times P_c \approx P$} -- in other words, if we split the entire graph into connected subgraphs, the number of subgraphs multiplied by the average number of nodes (contributors) per subgraph should equal the total number of contributors ($C$).
+This, however, is not the case.
+In fact, $P_c$ is notably smaller than expected.
+Recall that during analysis, subgraphs of {$< 3$} nodes were not considered.
+We can assume then that a large number of subgraphs are very small, with only one or two nodes.
+Further analysis is needed to fully understand the implications of this.
+
+To validate the hypothesis, we expect to find that intermediate values of $Q$ will be correlated with more popular projects.
 To explore this possibility, we first compare the popularity given $Q$ values as shown in figures \ref{fig:q_fc_graph} and \ref{fig:q_sf_graph}.
@@
 \end{center}
-\caption{$Q$ and Project Popularity}
+\caption{Freecode $Q$ and Project Popularity}
 \label{fig:q_fc_graph}
@@
 \end{center}
-\caption{$Q$ and Project Popularity}
+\caption{SourceForge $Q$ and Project Popularity}
 \label{fig:q_sf_graph}
@@
 \end{center}
-\caption{$Q$ Distribution}
+\caption{Freecode $Q$ Distribution}
 \label{fig:q_fc_distribution}
@@
 \end{center}
-\caption{$Q$ Distribution}
+\caption{SourceForge $Q$ Distribution}
 \label{fig:q_sf_distribution}
@@
 The research interviews provided a look into how some of these quantitative findings translate into actual industry practice.
-It also helped us to get a deeper understand of what what we have found in the data analysis, as we could begin to build some workplace context into our results.
-There were are few re-occurring themes that we will base our analysis on\cite{stmartin_interview,stmartin_interview}:
+It also helped us to get a deeper understanding of what we had found in the data analysis, as we could begin to build some workplace context into our results.
+There were are few re-occurring themes from which we will base our analysis\cite{stmartin_interview,rana_interview}:
 
@@
 \section{Conclusion}
-The project graph contains a large amount of subgraphs, and as a whole appears less clustered than some other observed social network graphs\cite{madey2002open}.
+Our hypothesis theorizes that medium values of clustering between collaborators on projects is optimal for project performance.
+The data analysis, specifically figures \ref{fig:q_fc_graph} and \ref{fig:q_sf_graph}, seem to support this claim.
+Also, qualitative research seems to support the hypothesis as well.
+Our interviews revealed that from experience, teams perform best when a stable core is periodically augmented with new members.
+This would be a qualitative representation of a intermediate $Q$ value -- significant clustering but not to the extent of isolation.
+Given both the quantitative and qualitative analysis, we can assert to align with Uzzi's findings\cite{uzzi2005collaboration} and show that intermediate values of $Q$ are correlated with increased project performance.
 
-A further area of study would be how this relates to previously defined \textit{success factors} in projects\cite{cooke2002real}.
+\section{Future Research}
+Social networks, interpersonal relationships, and software development are all complex topics.
+We have explored a narrow slice of these in context, and there are some important areas of future exploration.
+First, the contributor graph contains a large amount of subgraphs, and as a whole appears less clustered than some other observed social network graphs -- consistent with Madey's findings\cite{madey2002open} on SourceForge data.
+As noted in our analysis, a large number of these subgraphs have only one or two contributors.
+This implies that a large number of contributors work alone and on a single project.
+We do not, with the current analysis, know how (or if) this degrades the quality of our findings.\\
+
+A further area of study would be how our findings relate to previously defined \textit{success factors} in projects\cite{cooke2002real}.
+Also, we do not know directly \textit{how} intermediate values of $Q$ influence performance -- we can only observe a quantitative and qualitative correlation.
+We make a tacit equivalence to clustering and knowledge sharing, but we have not directly observed that in our analysis.
+Research does suggest that social factors are knowledge sharing motivators\cite{hendriks1999share}, but how that relates specifically to our work is unexplored here.\\
 

### 2013-11-30 code/analyze_graph.py

@@ -128,7 +128,7 @@ def compute_random_graph(nodes, edges, g):
         assert (edges == (nodes - 1))
         return g
 
-def graph(name, data, popularity):
+def graph(title, name, data, popularity):
     contributors = data[0]
     projects = data[1]
     G = nx.Graph()
@@ -210,7 +210,7 @@ def graph(name, data, popularity):
     total_projects = len(set(sum(contributors.values(), [])))
 
     write_table("subgraphs_summary_" + name,
-                table.create_table("Summary", "fig:summary_stats", "P: %s, $P_c$: %s, C: %s" % (total_projects, N, len(contributors.keys())),
+                table.create_table(title + " Summary", "fig:"+name+"_summary_stats", "P: %s, $P_c$: %s, C: %s" % (total_projects, N, len(contributors.keys())),
                                    OrderedDict([
                                        ("$Q$", q),
                                        ("$C^{\Delta}$", cc),
@@ -240,14 +240,18 @@ def create_graph(filename, x, y):
     avg = [np.mean(j, axis=None) for j in y]
     median = [np.median(j) for j in y]
 
-    fig = plt.figure()
-    plt.plot(x,avg,'-')
-    plt.plot(x,median,'--')
-    plt.xlabel("$Q$")
-    plt.ylabel("popularity")
+    fig, ax = plt.subplots()
+    ax.plot(x,avg,'k-', label="Mean")
+    ax.plot(x,median,'k--', label="Median")
+
+    ax.set_xlabel("$Q$")
+    ax.set_ylabel("popularity")
+
+    ax.legend(shadow=True)
+
     F = plt.gcf()
     F.savefig("../paper/images/"+filename+"-graph.png")
     plt.close(fig)
 
-graph("freecode", read_contributors_fc(), read_stats_fc())
-graph("sf", read_contributors_sf(), read_stats_sf())
+graph("Freecode", "freecode", read_contributors_fc(), read_stats_fc())
+graph("SourceForge", "sf", read_contributors_sf(), read_stats_sf())

### 2013-12-01 paper/main.tex
Rearranged and shuffled.

@@
 An interesting aspect of team building is the relationships formed between the team members.
-If follows that visualizing software team members as a graph can give some insight as to what the optimal team conditions are.
+It follows then that visualizing software team members as a graph may be a natural way to explore these relationships.
 As team members move between projects, these graphs become more and more connected as team members collaborate and form relationships.
@@
 A social network is a graph of people and the connections between them.
-The dynamics of social networks have proved to be an important research topic for many different areas of study, from academic publication\cite{barabasi2002evolution}, to the success of broadway musicals\cite{uzzi2005collaboration}.
-In general, a social network is important to understanding how ideas and influence are spread\cite{kempe2003maximizing}, from which we can investigate the best conditions for optimal group perfomance within these networks.
+The dynamics of social networks have proved to be an important research topic for many different areas of study, from academic publication\cite{barabasi2002evolution}, to the success of Broadway musicals\cite{uzzi2005collaboration}.
+In general, a social network is important to understanding how ideas and influence are spread\cite{kempe2003maximizing}.
+Given that, we can begin to investigate the best conditions for optimal group performance within these networks.
 
-A `small world' network is a social network characterized by high clustering of graph nodes paired with a short average path between nodes\cite{watts1998collective}.
-`Clustering' in this context means how closely nodes in the graph are related to each other, or "the friend of my friend is also my friend." Milgram, in is seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}, or in other words, the average `path length' between any two people.
+A ``small world'' network is a social network characterized by high clustering of graph nodes paired with a short average path between nodes\cite{watts1998collective}.
+``Clustering'' in this context means how closely nodes in the graph are related to each other, or ``the friend of my friend is also my friend.'' Milgram, in is seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}, or in other words, the average ``path length'' between any two people.
 
@@
 We hypothesize that the qualities of a small world graph that foster collaboration, creativity, and the efficiency of how knowledge is transfered\cite{latora2001efficient} will also apply to software project teams.
-In this work, we investigate the `small world' phenomenon quantitatively by exploring open source project data, and qualitatively by a series of interviews of subject matter experts, and look to compare Uzzi's findings to ours.
+In this work, we investigate the ``small world'' phenomenon quantitatively by exploring open source project data, and qualitatively by a series of interviews of subject matter experts, and look to compare Uzzi's findings to ours.
 
 \subsection{Hypothesis}
-The formalization of the `small world' quality of a graph can be expressed by the \textit{Small World Quotient}, or $Q$\cite{watts1999small,watts1998collective}.
+The formalization of the ``small world'' quality of a graph can be expressed by the \textit{Small World Quotient}, or $Q$\cite{watts1999small,watts1998collective}.
 The value $Q$ is calculated by dividing the clustering factor of graph by the average path length between nodes.
@@
 \subsection{Analysis}
-The collected data was organized into a graph structure, with the nodes representing the collaborators and the edges representing one or more shared project between collaborators.
-Various properties of the graph are analyzed, followed by a qualitative section to help link the quantitative analysis to subject matter expert experiences.
+The collected data was organized into a graph structure, with the nodes representing the contributors and the edges representing one or more shared project between contributors.
+For our purposes, ``contributors'' includes any person that has been identified as being associated with the project by the project hosting site (Freecode and SourceForge, for our purposes).
+It is important to note that contributor does not always imply code contributions -- as issue reporting and documentation, among other things, are valid contributions.
+Various properties of the graph were analyzed, followed by a qualitative section to help link the quantitative analysis to subject matter expert experiences.
 
@@
 
-The Freecode data can be represented as a bipartite graph.
+The contributor/project data can be represented as a bipartite graph.
 A bipartite graph is a specialized type of graph containing two disjoint sets of verticies.
@@
 
-We assume for throughout that any graph exhibiting {$Q > 1$} is a small-world graph.
+We assume for throughout that any graph exhibiting {$Q > 1$} is a small world graph.
 
@@
 For both datasets, we base our performance metric on \textit{use}.
-For Freecode, we use the \textit{Popularity Score} metric, which is calculated the following formula\footnote{http://help.freecode.com/kb/statistics/how-do-you-measure-a-projects-popularity}:
+For Freecode, we use the \textit{Popularity Score} metric, which is calculated by the following formula\footnote{http://help.freecode.com/kb/statistics/how-do-you-measure-a-projects-popularity}:
 
@@
 For the SourceForge dataset, performance is based on the repository's internal \textit{rank} metric.
+This metric ranks each project from 1 to the total number of projects in SourceForge ($P_{sf}$), or ${1 <= rank <= |P_{sf}|}$.
+At the time of this writing, no formula for the \textit{rank} metric could be located for citation.
 Note that there was no attempt to normalize the two performance metrics between datasets.
@@
 $E$ - \textit{Number of Edges}\\
-As measured over the number of projects $P$, with the total number of contributors $C$. The number of connected subgraphs analyzed is shown as $P_c$.
+As measured over the number of projects $P$, with the total number of contributors $C$.
+The number of connected subgraphs analyzed is shown as $P_c$.
+The connected subgraphs are the main unit of analysis, and each statistical operation is applied to the set of subgraphs $P_c$.
 
@@
 The median, however, is 1.0 in both cases, which does not match the small world network criteria.
-A possible explanation of this is the power law distribution of $Q$ observed in both data sets (figures \ref{fig:q_fc_distribution} and \ref{fig:q_sf_distribution}.
+A possible explanation of this is the power law distribution of $Q$ observed in both data sets (figures \ref{fig:q_fc_distribution} and \ref{fig:q_sf_distribution}).
 This indicates that a large proportion of $Q$ values are around 1.\\
@@
 This observation indicates a high degree of clustering\cite{watts1998collective}.
-hat any indicates that the majority of subgraphs have a $Q$ and $C^\Delta$ value of close to either 0 or 1.
 Exploring this phenomenon further, we can derive that most graphs resemble the middle or the bottom graph in figure \ref{fig:example_graphs}, with relatively few resembling the top graph.\\
@@
 Note that $P_c$ values are relatively small compared to $P$ and $C$ values.
-It would be intuitive to assume that {$C \times P_c \approx P$} -- in other words, if we split the entire graph into connected subgraphs, the number of subgraphs multiplied by the average number of nodes (contributors) per subgraph should equal the total number of contributors ($C$).
+It would be intuitive to assume that {$N \times P_c \approx C$} -- in other words, if we split the entire graph into connected subgraphs, the number of subgraphs ($P_c$) multiplied by the average number of nodes ($N$) per subgraph should equal the total number of contributors ($C$).
 This, however, is not the case.
@@
 
-Small-world-ness, or $Q$, is generally between 1 and 3 for most sub-graphs.
-
 \subsection{Qualitative}
 The research interviews provided a look into how some of these quantitative findings translate into actual industry practice.
-It also helped us to get a deeper understanding of what we had found in the data analysis, as we could begin to build some workplace context into our results.
+It also helped us to obtain a deeper understanding of what we had found in the data analysis, as we could begin to build some workplace context into our results.
 There were are few re-occurring themes from which we will base our analysis\cite{stmartin_interview,rana_interview}:
@@
 A highly static team (or, a team with a high $Q$ value), runs the risk of falling behind the technology trends.
+Occasional new members (or, intermediate values of $Q$) was perceived as a positive in terms of information flow
 
@@
 
-\section{Future Research}
+\section{Discussion and Future Research}
 Social networks, interpersonal relationships, and software development are all complex topics.

### 2013-12-03 paper/main.tex
First proof-read run.

@@
 An interesting aspect of team building is the relationships formed between the team members.
-It follows then that visualizing software team members as a graph may be a natural way to explore these relationships.
+Because of these relationships, visualizing software team members as a graph may be a natural way to explore these relationships.
 As team members move between projects, these graphs become more and more connected as team members collaborate and form relationships.
@@
 A ``small world'' network is a social network characterized by high clustering of graph nodes paired with a short average path between nodes\cite{watts1998collective}.
-``Clustering'' in this context means how closely nodes in the graph are related to each other, or ``the friend of my friend is also my friend.'' Milgram, in is seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}, or in other words, the average ``path length'' between any two people.
+``Clustering'' in this context means how closely nodes in the graph are related to each other, or ``the friend of my friend is also my friend.'' ``Average path length'' is the the shortest route between all possible nodes, averaged over the entire graph.
+Milgram, in his seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}, or in other words, the average path length between any two people.
 
@@
 In his study, the network of artists involved in the making of Broadway musicals from 1945 to 1989 were studied.
-Performance of the musicals were then measured based on financial success and critical acclaim, and compared that quantitative analysis to the clustering and path length of the graph.
+Performance was then measured based on financial success and critical acclaim, and statistically compared to the clustering and path length of the graph.
 
@@
 Data was collected using the freely available FLOSSmole\cite{floss2006} data sets of free and open source projects.
-Two datasets were analyzed -- data from from the popular open source project site \textit{Freecode},\footnote{http://freecode.com/}, and another from open source software repository \textit{SourceForge}.
+Two datasets were analyzed -- data from from the popular open source project site \textit{Freecode}\footnote{http://freecode.com/}, and another from open source software repository \textit{SourceForge}\footnote{http://sourceforge.net/}.
 The Freecode dataset contained data up to September, 2013, while the SourceForge dataset was slightly older with data gathered on June 2009.
-Both datasets were chosen because they met two basic criteria: (1) they contained an exhaustive list of projects and contributors to those projects, and (2) they provided some sort of quantitative measure of project ``popularity." This popularity metric will be further described in sectiions below.
+Both datasets were chosen because they met two basic criteria: (1) they contained an exhaustive list of projects and contributors to those projects, and (2) they provided some sort of quantitative measure of project ``popularity." This popularity metric will be further described in sections below.
 Results were analyzed using the Python graph processing packaged NetworkX\cite{hagberg-2008-exploring}.
@@
 For our purposes, ``contributors'' includes any person that has been identified as being associated with the project by the project hosting site (Freecode and SourceForge, for our purposes).
-It is important to note that contributor does not always imply code contributions -- as issue reporting and documentation, among other things, are valid contributions.
+It is important to note that ``contributor'' does not always imply code contributions -- as issue reporting and documentation, among other things, are valid contributions.
 Various properties of the graph were analyzed, followed by a qualitative section to help link the quantitative analysis to subject matter expert experiences.
@@
 For each dataset, we first considered the dataset to be one large graph.
-From this large disconnected graph, each connected subgraph was analyzed.
+It was observed that the contributor graph was ``disconnected,'' meaning that there was not a path between all possible nodes.
+From this large disconnected graph, we can extract a set of connected subgraphs, where each connected subgraph was analyzed.
 Metrics were then computed for each of these subgraphs.
@@
 This would have led to a graph with nodes of projects $P$, each being linked by sharing a common contributor.
-This approach is a common way of representing these bipartite graphs\cite{newman2001scientific}, and illustrates the fact that a bipartite projections are lossy compared to the data represented in the original graph\cite{zhou2007bipartite}.\\
+This approach is a common way of representing these bipartite graphs\cite{newman2001scientific}, although it is known that bipartite projections are lossy compared to the data represented in the original graph\cite{zhou2007bipartite}.\\
 
@@
 \subsubsection{Graph Analysis}
-To support our hypotheses, there are several key metrics to be studied in regards to the aforementioned graph.
+To support our hypothesis, there are several key metrics to be studied in regards to the aforementioned graph.
 Many of these metrics follow the work of Boccaletti \textit{et.
@@
 \noindent\\\textit{\textbf{Average Path Length ($L$)}}\\
-Also, calculating the \textit{Path Length} ($L$) allows us to determine how far removed developers in the graph are from one another.
+Calculating the \textit{Path Length} ($L$) allowed us to determine how far removed contributors in the graph are from one another.
 The path length is calculated as the average distance between any two node pairs in the graph:
@@
 Where {$v_i \in P$}, {$v_j \in P$}, and {$\lambda(v_i,v_j)$} denotes the shortest path between the two nodes.
-We only consider path length for connected subgraphs, avoiding some complexities of this calculation on disconnected graphs\cite{boccaletti2006complex}.
+We only considered path length for connected subgraphs, avoiding some complexities of this calculation on disconnected graphs\cite{boccaletti2006complex}.
 
@@
 This idea of homophily, however, needs to be further expanded before we can make assertions about correlations to performance.
-It has been shown that demographic homophily is complex to measure, correlates little to performance outcomes, and in fact correlate negatively\cite{reagans2004make,lawrence1997perspective}.
+It has been shown that demographic homophily is complex to measure, correlates little to performance outcomes, and in fact correlates negatively\cite{reagans2004make,lawrence1997perspective}.
 For our purposes, it is much more appropriate to examine how teams best leverage similarities of knowledge and information, as the flow of these assets can be a key driver to success\cite{nissen2002extended}.\\
@@
 Both have had experience with project management and are certified Project Management Professionals (PMP)\textregistered.
-We proposed to them the following questions, in hopes of expanding further the questions posed above:
+We proposed to them the following questions, with the intent of expanding further the questions posed above:
 
@@
 $E$ - \textit{Number of Edges}\\
-As measured over the number of projects $P$, with the total number of contributors $C$.
+The results shown were as measured over the number of projects $P$, with the total number of contributors $C$.
 The number of connected subgraphs analyzed is shown as $P_c$.
@@
 
-A mean value of $Q$ was observed to be $> 1$ for both data sets, which meets the criteria for a small-world network\cite{humphries2008network}.
+A mean value of $Q$ was observed to be $> 1$ for both data sets, which meets the criteria for a small world network\cite{humphries2008network}.
 The median, however, is 1.0 in both cases, which does not match the small world network criteria.
@@
 Note that $P_c$ values are relatively small compared to $P$ and $C$ values.
-It would be intuitive to assume that {$N \times P_c \approx C$} -- in other words, if we split the entire graph into connected subgraphs, the number of subgraphs ($P_c$) multiplied by the average number of nodes ($N$) per subgraph should equal the total number of contributors ($C$).
+It would be intuitive to assume that {$N \times P_c \approx C$} -- in other words, if we split the entire graph into connected subgraphs, the number of subgraphs ($P_c$) multiplied by the average number of nodes ($N$) per subgraph should approximately equal the total number of contributors ($C$).
 This, however, is not the case.
@@
 To explore this possibility, we first compare the popularity given $Q$ values as shown in figures \ref{fig:q_fc_graph} and \ref{fig:q_sf_graph}.
-The $Q$ values do display the U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi \textit{et.
+The $Q$ values do display the inverse U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi \textit{et.
 al}\cite{uzzi2005collaboration}.
@@
 The research interviews provided a look into how some of these quantitative findings translate into actual industry practice.
-It also helped us to obtain a deeper understanding of what we had found in the data analysis, as we could begin to build some workplace context into our results.
+They also helped us to obtain a deeper understanding of what we had found in the data analysis, as we could begin to build some workplace context into our results.
 There were are few re-occurring themes from which we will base our analysis\cite{stmartin_interview,rana_interview}:
@@
 Notably, has been suggested that individual performance in a group is highest if that individual is not in the core or the periphery, but somewhere in between\cite{cattani2008core}.
-This is especially interesting as this aligns with our hypothesis that intermediate values of $Q$ are optimal.
+This is especially interesting as it aligns in principle with our hypothesis that intermediate values of $Q$ are optimal.
 
@@
 A highly static team (or, a team with a high $Q$ value), runs the risk of falling behind the technology trends.
-Occasional new members (or, intermediate values of $Q$) was perceived as a positive in terms of information flow
+Occasional new members (or, intermediate values of $Q$) were perceived as a positive in terms of information flow.
 
@@
 Clear goals and a common objective were positive influencer, while continuously shifting focus was a negative influence.
-Research in this area suggests that creative teams have ``goals that are clear and compelling, but also open and challenging''\cite{isaksen2002climate}.
+Research in this area suggests that creative teams have ``goals that are clear and compelling, but also open and challenging.''\cite{isaksen2002climate}
 
-Timeline and priority discussed as strong contributors to team success.
-Team building could be thought of as function of the timeline, meaning that as the timeline of the project increased, more time could be devoted to team building activities.
+Timeline and priority were discussed as strong factors in team success.
+Team building could be thought of as function of the timeline -- meaning that as the timeline of the project increased, more time could be devoted to team building activities.
 
@@
 
-\section{Discussion and Future Research}
+\section{Future Research}
 Social networks, interpersonal relationships, and software development are all complex topics.

### 2013-12-05 paper/interview1.tex
Proofread.

@@
 
-\subsection*{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project.}
+\subsection*{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project?}
 Familiarity is good, but you have to account for burnout if people work on the same project for too long.

### 2013-12-05 paper/interview2.tex
Proofread.

@@
 
-\subsection*{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project.}
+\subsection*{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project?}
 This really depends on the time-line of the project.

### 2013-12-05 paper/main.tex
Proofread.

@@
 \begin{abstract}
-Team cohesion and the dynamics of team forming are important parts of any project, with software projects being no exception.
+Team cohesion and the dynamics of team formation are important parts of any project, with software projects being no exception.
 An interesting aspect of team building is the relationships formed between the team members.
@@
 A social network is a graph of people and the connections between them.
-The dynamics of social networks have proved to be an important research topic for many different areas of study, from academic publication\cite{barabasi2002evolution}, to the success of Broadway musicals\cite{uzzi2005collaboration}.
+The dynamics of social networks have proven to be an important research topic for many different areas of study, from academic publication\cite{barabasi2002evolution}, to the success of Broadway musicals\cite{uzzi2005collaboration}.
 In general, a social network is important to understanding how ideas and influence are spread\cite{kempe2003maximizing}.
@@
 
-A ``small world'' network is a social network characterized by high clustering of graph nodes paired with a short average path between nodes\cite{watts1998collective}.
-``Clustering'' in this context means how closely nodes in the graph are related to each other, or ``the friend of my friend is also my friend.'' ``Average path length'' is the the shortest route between all possible nodes, averaged over the entire graph.
-Milgram, in his seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}, or in other words, the average path length between any two people.
+A ``small world'' network is a social network characterized by high clustering of graph nodes paired with a short average path between them\cite{watts1998collective}.
+``Clustering'' in this context means how closely nodes in the graph are related to each other, or ``the friend of my friend is also my friend.'' ``Average path length'' is the shortest route between all possible nodes, averaged over the entire graph.
+Milgram, in his seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}, or in other words, the average path length between any two people is 6.
 
@@
 \subsection{Collection and Storage}
-Data was collected using the freely available FLOSSmole\cite{floss2006} data sets of free and open source projects.
+Data was collected using the freely available FLOSSmole\cite{floss2006} datasets of free and open source projects.
 Two datasets were analyzed -- data from from the popular open source project site \textit{Freecode}\footnote{http://freecode.com/}, and another from open source software repository \textit{SourceForge}\footnote{http://sourceforge.net/}.
@@
 The collected data was organized into a graph structure, with the nodes representing the contributors and the edges representing one or more shared project between contributors.
-For our purposes, ``contributors'' includes any person that has been identified as being associated with the project by the project hosting site (Freecode and SourceForge, for our purposes).
+For our purposes, ``contributors'' includes any person that has been identified as being associated with the project by the project hosting site (Freecode and SourceForge).
 It is important to note that ``contributor'' does not always imply code contributions -- as issue reporting and documentation, among other things, are valid contributions.
@@
 It was observed that the contributor graph was ``disconnected,'' meaning that there was not a path between all possible nodes.
-From this large disconnected graph, we can extract a set of connected subgraphs, where each connected subgraph was analyzed.
+From this large disconnected graph, we extracted a set of connected subgraphs, where each connected subgraph was analyzed.
 Metrics were then computed for each of these subgraphs.
@@
 This can be denoted by ${G=(P,C,E)}$, where ${P \cap C = \emptyset}$.
-For our purposes, let set $P$ be the set of all projects, and set $C$ be the set of all contributors.
+For our purposes, let set $P$ be the set of all projects, set $C$ be the set of all contributors, and $E$ the edges that connect them.
 Each project node, therefore, is only connected to contributor nodes, and vice versa, as show in figure \ref{fig:example_bipartite_graph}.
+In other words, the sets $P$ and $C$ are disjoint.
 This bipartite representation is typical of what is found in social and collaboration networks\cite{ramasco2004self}.
@@
 Here, contributors are connected directly, with edges occurring if a two contributors share one or more common projects.
-It is important to note that the projection could have been done in terms of the projects, not the contributors.
+It is important to note that the projection could have been done in terms of the projects, instead of the contributors.
 This would have led to a graph with nodes of projects $P$, each being linked by sharing a common contributor.
-This approach is a common way of representing these bipartite graphs\cite{newman2001scientific}, although it is known that bipartite projections are lossy compared to the data represented in the original graph\cite{zhou2007bipartite}.\\
+Projection is a common way of representing these bipartite graphs\cite{newman2001scientific}, although it is known that bipartite projections are lossy compared to the data represented in the original graph\cite{zhou2007bipartite}.\\
 
@@
 \noindent\\\textit{\textbf{Clustering Coefficient - Transitivity ($C^\Delta$)}}\\
-We calculate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
+We calculate the \textit{Clustering Coefficient} ($C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
 \[C^\Delta = 3 \times \frac{\text{number of triangles}}
@@
 It is also the probability that two nodes will be connected if they share a common neighbor\cite{newman2003properties}.
-In our context, if contributors $C_1$ and $C_2$ both collaborate with a common contributor w $C_3$, this metric represents the probability that $C_1$ and $C_2$ will collaborate.
+In our context, if contributors $C_1$ and $C_2$ both collaborate with a common contributor $C_3$, this metric represents the probability that $C_1$ and $C_2$ will collaborate.
 
@@
 
-From this \textit{Local Clustering Coefficient} $C_i$, we can then take the average over the entire set of nodes in the graph.
+From this \textit{Local Clustering Coefficient} $C^{\lambda}_i$, we can then take the average over the entire set of nodes in the graph.
 \[ \overline{C^\lambda} = \frac{1}{|P|}\sum^{|P|}_{i=1}C^{\lambda}_i \]
@@
 
-Where {$v_i \in P$}, {$v_j \in P$}, and {$\lambda(v_i,v_j)$} denotes the shortest path between the two nodes.
+Where given {$v_i \in P$}, {$v_j \in P$}, the function {$\lambda(v_i,v_j)$} denotes the shortest path between the two nodes.
 We only considered path length for connected subgraphs, avoiding some complexities of this calculation on disconnected graphs\cite{boccaletti2006complex}.
@@
 
-We assume for throughout that any graph exhibiting {$Q > 1$} is a small world graph.
+We assume throughout that any graph exhibiting {$Q > 1$} is a small world graph.
 
@@
 To further study these factors, we arranged interviews with two current professionals in the field.
-Both have had experience with project management and are certified Project Management Professionals (PMP)\textregistered.
+Both have had experience with project management and are certified Project Management Professionals (PMP\textregistered).
 We proposed to them the following questions, with the intent of expanding further the questions posed above:
@@
 \noindent\\\textit{Q2: Do teams generally remain intact over multiple projects, or do members often shuffle and re-combine?}\\
-\noindent\\\textit{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project.}\\
+\noindent\\\textit{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project?}\\
 \noindent\\\textit{Q4: What are some characteristics of a high performing team?}\\
@@
 
-Summary statistics for the graph analysis are captured in figure \ref{fig:summary_stats}.  Statistics analyzed included:\\
+Summary statistics for the graph analysis are captured in tables \ref{fig:freecode_summary_stats} and \ref{fig:sf_summary_stats}.  Statistics analyzed included:\\
 $Q$ - \textit{Small World Quotient}\\
@@
 The values of $Q$ generally follow a power-law distribution, with most values being at our around {$Q = 1$}.
-This indicates that many graphs are close to the delineation of being considered small-world\cite{humphries2008network}.
+This indicates that many graphs are close to the delineation of being considered small world\cite{humphries2008network}.
 
@@
 They also helped us to obtain a deeper understanding of what we had found in the data analysis, as we could begin to build some workplace context into our results.
-There were are few re-occurring themes from which we will base our analysis\cite{stmartin_interview,rana_interview}:
+There were several re-occurring themes from which we will base our analysis\cite{stmartin_interview,rana_interview}:
 
@@
 It was also indicated that priority was a major factor.
-Different project priorities, and the resultant shifting of resources, had the possible effect of the weakening of string team's core members.
+Different project priorities, and the resultant shifting of resources, had the possible effect of weakening a strong team's core members.
 This can be related to focus as well, as changing priorities can cause resource realignment and decreased overall focus.

### 2013-12-06 paper/main.tex
One more proofreading pass.

@@
 This indicates that there is an optimal ratio of new and familiar members on a team -- or, an optimal value of $Q$ when related to performance.
+Thus, we formulate our hypothesis:\\
 
@@
 \subsection{Collection and Storage}
-Data was collected using the freely available FLOSSmole\cite{floss2006} datasets of free and open source projects.
-Two datasets were analyzed -- data from from the popular open source project site \textit{Freecode}\footnote{http://freecode.com/}, and another from open source software repository \textit{SourceForge}\footnote{http://sourceforge.net/}.
-The Freecode dataset contained data up to September, 2013, while the SourceForge dataset was slightly older with data gathered on June 2009.
+To explore our hypothesis, software project data was collected and analyzed.
+This data was collected using the freely available FLOSSmole\cite{floss2006} datasets of free and open source projects.
+Two datasets were analyzed -- data from from the popular open source project site \textit{Freecode},\footnote{http://freecode.com/} and another from open source software repository \textit{SourceForge}.\footnote{http://sourceforge.net/} The Freecode dataset contained data up to September 2013, while the SourceForge dataset was slightly older with data gathered up to June 2009.
 Both datasets were chosen because they met two basic criteria: (1) they contained an exhaustive list of projects and contributors to those projects, and (2) they provided some sort of quantitative measure of project ``popularity." This popularity metric will be further described in sections below.
-Results were analyzed using the Python graph processing packaged NetworkX\cite{hagberg-2008-exploring}.
+Results were analyzed using the Python graph processing package NetworkX\cite{hagberg-2008-exploring}.
 All source code pertaining to the collection and analysis can be found at \url{https://github.com/kevinpeterson/small-world-effect-research}.
@@
 This implies a subgraph of {$>= 3$} nodes is needed.
-Subgraphs of {$< 3$} nodes were not considered for analysis.
+Because of this, subgraphs of {$< 3$} nodes were not considered for analysis.
 
@@
 This would have led to a graph with nodes of projects $P$, each being linked by sharing a common contributor.
-Projection is a common way of representing these bipartite graphs\cite{newman2001scientific}, although it is known that bipartite projections are lossy compared to the data represented in the original graph\cite{zhou2007bipartite}.\\
+Projection is a common way of representing these bipartite graphs\cite{newman2001scientific}, although it is known that bipartite projections are lossy compared to the data represented in the original graph\cite{zhou2007bipartite}.
 
@@
 Another approach to clustering is to take the average of each node's local clustering coefficient\cite{watts1998collective}.
+To calculate the local clustering coefficient of a node, we follow these steps:
 
@@
 From this \textit{Local Clustering Coefficient} $C^{\lambda}_i$, we can then take the average over the entire set of nodes in the graph.
-\[ \overline{C^\lambda} = \frac{1}{|P|}\sum^{|P|}_{i=1}C^{\lambda}_i \]
+\[ \overline{C^\lambda} = \frac{1}{|P|}\sum_{i \in P}C^{\lambda}_i \]
 
@@
 \noindent\\\textit{\textbf{Small World Quotient ($Q$)}}\\
-The definition of a \textit{small world} graph can be formalized by the following equations\cite{humphries2008network,uzzi2005collaboration}.
+The definition of a \textit{small world} graph can be formalized by the following equations\cite{humphries2008network,uzzi2005collaboration}:
 
@@
 
-Finally, the ratio of the above calculations yields the small world quotient, or $Q$, of the graph
+Finally, the ratio of the above calculations yields the small world quotient, or $Q$, of the graph.
 \[Q = \frac{\gamma^{\Delta}_g }{\lambda_g} \]
@@
 To further explore the data, a measurement of project performance was needed.
-As the explored datasets consisted entirely of open source projects, research indicates that \textit{quality}, \textit{use}, \textit{user satisfaction}, and \textit{impact} are possible metrics to measure performance or \textit{success}\cite{crowston2003defining}.\\
+As the explored datasets consisted entirely of open source projects, research indicates that \textit{quality}, \textit{use}, \textit{user satisfaction}, and \textit{impact} are each possible metrics to measure performance or \textit{success}\cite{crowston2003defining}.\\
 
-For both datasets, we base our performance metric on \textit{use}.
-For Freecode, we use the \textit{Popularity Score} metric, which is calculated by the following formula\footnote{http://help.freecode.com/kb/statistics/how-do-you-measure-a-projects-popularity}:
+For both datasets, we based our performance metric on \textit{use}.
+For Freecode, we used the \textit{Popularity Score} metric, which is calculated by the following formula:\footnote{http://help.freecode.com/kb/statistics/how-do-you-measure-a-projects-popularity}
 
@@
 
-For the SourceForge dataset, performance is based on the repository's internal \textit{rank} metric.
+For the SourceForge dataset, performance was based on the repository's internal \textit{rank} metric.
 This metric ranks each project from 1 to the total number of projects in SourceForge ($P_{sf}$), or ${1 <= rank <= |P_{sf}|}$.
@@
 We have said little as to why these connections are made, how they are maintained, and what exactly a connection means at a personal level.
-Via qualitative analysis, we will attempt to enrich our data analysis by providing deeper context.\\
+Via qualitative analysis, we will attempt to enrich our data analysis by providing deeper context.
+
 A connection between two people is much more than an edge between two nodes in a graph.
@@
 It has been shown that demographic homophily is complex to measure, correlates little to performance outcomes, and in fact correlates negatively\cite{reagans2004make,lawrence1997perspective}.
-For our purposes, it is much more appropriate to examine how teams best leverage similarities of knowledge and information, as the flow of these assets can be a key driver to success\cite{nissen2002extended}.\\
+For our purposes, it is much more appropriate to examine how teams best leverage similarities of knowledge and information, as the flow of these assets can be a key driver to success\cite{nissen2002extended}.
+
 In the same way we can explore the role of team familiarity.
 The two types of familiarity that we will explore are \textit{member} familiarity and \textit{task/project} familiarity\cite{harrison2003time}.
-These metrics, although not captured in data, could be important factors in \textit{how} teams form, and thus help us to understand \textit{why} teams perform the way that they do.\\
+These metrics, although not captured in data, could be important factors in \textit{how} teams form, and thus help us to understand \textit{why} teams perform the way that they do.
 
@@
 A possible explanation of this is the power law distribution of $Q$ observed in both data sets (figures \ref{fig:q_fc_distribution} and \ref{fig:q_sf_distribution}).
-This indicates that a large proportion of $Q$ values are around 1.\\
+This indicates that a large proportion of $Q$ values are around 1.
 
@@
 This observation indicates a high degree of clustering\cite{watts1998collective}.
-Exploring this phenomenon further, we can derive that most graphs resemble the middle or the bottom graph in figure \ref{fig:example_graphs}, with relatively few resembling the top graph.\\
+Exploring this phenomenon further, we can derive that most graphs resemble the middle or the bottom graph in figure \ref{fig:example_graphs}, with relatively few resembling the top graph.
 
@@
 We can assume then that a large number of subgraphs are very small, with only one or two nodes.
-Further analysis is needed to fully understand the implications of this.
+Further analysis is needed to fully understand the implications of this observation.
 
@@
 To explore this possibility, we first compare the popularity given $Q$ values as shown in figures \ref{fig:q_fc_graph} and \ref{fig:q_sf_graph}.
-The $Q$ values do display the inverse U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi \textit{et.
-al}\cite{uzzi2005collaboration}.
+The $Q$ values do display the inverse U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi\cite{uzzi2005collaboration}.
 
@@
 Focus was specifically called out as an indicator of performance in one interview.
-Clear goals and a common objective were positive influencer, while continuously shifting focus was a negative influence.
+Clear goals and a common objective were positive influencers, while continuously shifting focus was a negative influence.
 Research in this area suggests that creative teams have ``goals that are clear and compelling, but also open and challenging.''\cite{isaksen2002climate}
 
-Timeline and priority were discussed as strong factors in team success.
+Timeline was discussed as a strong factor in team success.
 Team building could be thought of as function of the timeline -- meaning that as the timeline of the project increased, more time could be devoted to team building activities.
@@
 This implies that a large number of contributors work alone and on a single project.
-We do not, with the current analysis, know how (or if) this degrades the quality of our findings.\\
+We do not, with the current analysis, know how (or if) this degrades the quality of our findings.
 
@@
 We make a tacit equivalence to clustering and knowledge sharing, but we have not directly observed that in our analysis.
-Research does suggest that social factors are knowledge sharing motivators\cite{hendriks1999share}, but how that relates specifically to our work is unexplored here.\\
+Research does suggest that social factors are knowledge sharing motivators\cite{hendriks1999share}, but how that relates specifically to our work is unexplored here.
 

### 2013-12-06 paper/main.tex
One more proofreading pass.

@@
 An interesting aspect of team building is the relationships formed between the team members.
-Because of these relationships, visualizing software team members as a graph may be a natural way to explore these relationships.
-As team members move between projects, these graphs become more and more connected as team members collaborate and form relationships.
+Because of these relationships, representing software team members as a graph may be a natural way to explore these relationships.
+As team members move between projects, these graphs become more and more connected as team members collaborate and form new relationships.
 We show that this connectivity, known as the ``small world effect," has a positive impact on team performance when the connectivity levels are moderate.
@@
 ``Clustering'' in this context means how closely nodes in the graph are related to each other, or ``the friend of my friend is also my friend.'' ``Average path length'' is the shortest route between all possible nodes, averaged over the entire graph.
-Milgram, in his seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}, or in other words, the average path length between any two people is 6.
+For example, Milgram, in his seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}, or in other words, the average path length between any two people is 6.
 
 Uzzi \cite{uzzi2005collaboration} expanded on this by exploring how these small world networks correlate to collaboration and creativity.
-In his study, the network of artists involved in the making of Broadway musicals from 1945 to 1989 were studied.
+In his study, the network of artists involved in the making of Broadway musicals from 1945 to 1989 were analyzed.
 Performance was then measured based on financial success and critical acclaim, and statistically compared to the clustering and path length of the graph.
@@
 Productions are less likely to be successful when team members are very familiar with each other.
-Also, probability of success drops much the same way when there is little familiarity between team members.
+Also, the probability of success drops much the same way when there is little familiarity between team members.
 This indicates that there is an optimal ratio of new and familiar members on a team -- or, an optimal value of $Q$ when related to performance.
@@
 
-Given our graph of nodes $P$ connected by edges $E$, or ${G=(P,E)}$, for any given node we can determine its \textit{neighborhood} ($N_i$), or the set of nodes directly connected to a given node.
-\[ N_i = \{v_j : e_{ij} \in E \wedge e_{ji} \in E \wedge v_j \in P\} \]
+Given our graph of nodes $C$ connected by edges $E$, or ${G=(C,E)}$, for any given node we can determine its \textit{neighborhood} ($N_i$), or the set of nodes directly connected to a given node.
+\[ N_i = \{v_j : e_{ij} \in E \wedge e_{ji} \in E \wedge v_j \in C\} \]
 
@@
 From this \textit{Local Clustering Coefficient} $C^{\lambda}_i$, we can then take the average over the entire set of nodes in the graph.
-\[ \overline{C^\lambda} = \frac{1}{|P|}\sum_{i \in P}C^{\lambda}_i \]
+\[ \overline{C^\lambda} = \frac{1}{|C|}\sum_{i \in C}C^{\lambda}_i \]
 
@@
 
-\[L = \frac{1}{|P| \cdot (|P|-1)} \sum_{i \neq j}\lambda(v_i,v_j)\]
+\[L = \frac{1}{|C| \cdot (|C|-1)} \sum_{i \neq j}\lambda(v_i,v_j)\]
 
-Where given {$v_i \in P$}, {$v_j \in P$}, the function {$\lambda(v_i,v_j)$} denotes the shortest path between the two nodes.
+Where given {$v_i \in C$}, {$v_j \in C$}, the function {$\lambda(v_i,v_j)$} denotes the shortest path between the two nodes.
 We only considered path length for connected subgraphs, avoiding some complexities of this calculation on disconnected graphs\cite{boccaletti2006complex}.
@@
 To further explore the data, a measurement of project performance was needed.
-As the explored datasets consisted entirely of open source projects, research indicates that \textit{quality}, \textit{use}, \textit{user satisfaction}, and \textit{impact} are each possible metrics to measure performance or \textit{success}\cite{crowston2003defining}.\\
+As the explored datasets consisted entirely of open source projects, research indicates that \textit{quality}, \textit{use}, \textit{user satisfaction}, and \textit{impact} are each possible metrics to measure performance or \textit{success}\cite{crowston2003defining}.
 

### 2013-12-06 paper/main.tex
One more proofreading pass.

@@
 An interesting aspect of team building is the relationships formed between the team members.
-Because of these relationships, representing software team members as a graph may be a natural way to explore these relationships.
+Because of these relationships, representing software team members as a graph may be a natural way to explore team dynamics.
 As team members move between projects, these graphs become more and more connected as team members collaborate and form new relationships.
@@
 The formalization of the ``small world'' quality of a graph can be expressed by the \textit{Small World Quotient}, or $Q$\cite{watts1999small,watts1998collective}.
-The value $Q$ is calculated by dividing the clustering factor of graph by the average path length between nodes.
+The value $Q$ is calculated by dividing the clustering factor of a graph by the average path length between nodes.
 Uzzi explored this value in graphs of Broadway productions\cite{uzzi2005collaboration}.
@@
 This data was collected using the freely available FLOSSmole\cite{floss2006} datasets of free and open source projects.
-Two datasets were analyzed -- data from from the popular open source project site \textit{Freecode},\footnote{http://freecode.com/} and another from open source software repository \textit{SourceForge}.\footnote{http://sourceforge.net/} The Freecode dataset contained data up to September 2013, while the SourceForge dataset was slightly older with data gathered up to June 2009.
+Two datasets were analyzed -- data from from the popular open source project site \textit{Freecode},\footnote{http://freecode.com/} and another from the open source software repository \textit{SourceForge}.\footnote{http://sourceforge.net/} The Freecode dataset contained data up to September 2013, while the SourceForge dataset was slightly older with data gathered up to June 2009.
 Both datasets were chosen because they met two basic criteria: (1) they contained an exhaustive list of projects and contributors to those projects, and (2) they provided some sort of quantitative measure of project ``popularity." This popularity metric will be further described in sections below.
@@
 \noindent\\\textit{\textbf{Average Path Length ($L$)}}\\
-Calculating the \textit{Path Length} ($L$) allowed us to determine how far removed contributors in the graph are from one another.
+Calculating the \textit{Average Path Length} ($L$) allowed us to determine how far removed contributors in the graph are from one another.
 The path length is calculated as the average distance between any two node pairs in the graph:
@@
 The median, however, is 1.0 in both cases, which does not match the small world network criteria.
-A possible explanation of this is the power law distribution of $Q$ observed in both data sets (figures \ref{fig:q_fc_distribution} and \ref{fig:q_sf_distribution}).
+A possible explanation of this is the power-law distribution of $Q$ observed in both data sets (figures \ref{fig:q_fc_distribution} and \ref{fig:q_sf_distribution}).
 This indicates that a large proportion of $Q$ values are around 1.
@@
 This observation indicates a high degree of clustering\cite{watts1998collective}.
-Exploring this phenomenon further, we can derive that most graphs resemble the middle or the bottom graph in figure \ref{fig:example_graphs}, with relatively few resembling the top graph.
+Exploring this phenomenon further, we can derive that most graphs conceptually resemble the middle or the bottom graph in figure \ref{fig:example_graphs}, with relatively few resembling the top graph.
 
@@
 \noindent\\\textit{\textbf{New contributors are good, as long as the core team remains intact.}}\\
-Both participants mentioned the idea of keeping a ``core" team intact.
-This was certainly an often cited notion in both interviews.
+Both participants mentioned the idea of keeping a ``core" team intact, and was an often cited concept in both interviews.
 This concept appears to align with the idea of a \textit{core/periphery}\cite{borgatti2000models}, where the graph under study contains one (or many) tightly interconnected subgraphs, with less tightly connected nodes radiating out from this core.
@@
 The data analysis, specifically figures \ref{fig:q_fc_graph} and \ref{fig:q_sf_graph}, seem to support this claim.
-Also, qualitative research seems to support the hypothesis as well.
+Also, our qualitative research tends to support the hypothesis as well.
 Our interviews revealed that from experience, teams perform best when a stable core is periodically augmented with new members.

### 2013-12-06 paper/main.tex
Submitted.

@@
 To validate the hypothesis, we expect to find that intermediate values of $Q$ will be correlated with more popular projects.
-To explore this possibility, we first compare the popularity given $Q$ values as shown in figures \ref{fig:q_fc_graph} and \ref{fig:q_sf_graph}.
-The $Q$ values do display the inverse U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi\cite{uzzi2005collaboration}.
+To explore this possibility, we compare the popularity given $Q$ values as shown in figures \ref{fig:q_fc_graph} and \ref{fig:q_sf_graph}.
+The $Q$ values do display the inverse U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi\cite{uzzi2005collaboration}, and supports our hypothesis.
 
@@
 \noindent\\\textit{\textbf{New contributors are good, as long as the core team remains intact.}}\\
-Both participants mentioned the idea of keeping a ``core" team intact, and was an often cited concept in both interviews.
+Both participants mentioned the idea of keeping a ``core" team intact, and it was an often cited concept in both interviews.
 This concept appears to align with the idea of a \textit{core/periphery}\cite{borgatti2000models}, where the graph under study contains one (or many) tightly interconnected subgraphs, with less tightly connected nodes radiating out from this core.
